---
title: "behavior-anlaysis"
author: "CEB"
date: '2025-11-26'
output: html_document
---


##load packages
```{r, warning = FALSE, message = FALSE, results = FALSE}
library(tidyverse) #for everything

library(cowplot) #for combining plots

#for bayesian modelling and interpreting:
library(brms)
library(tidybayes)
library(emmeans)
library(modelr)

```


#load data
```{r, warning = FALSE, message = FALSE, results = FALSE}
behav_dat_w_site<-read.csv("../data/behav_w_site_dat.csv")
behav_dat_w_site

```


###add in stegastes chases:
```{r, warning = FALSE, message = FALSE, results = FALSE}
behav_dat_w_site<-
behav_dat_w_site%>%
  mutate(Stegastes_binary_chases = case_when(grepl('Stegastes', Chases_during_observation, ignore.case = TRUE)~"yes",
                                            TRUE~"no"))%>%
  relocate(Stegastes_binary_chases, .after = Binary_chases)%>%
    mutate(Surgeonfish_binary_chases = case_when(grepl('Acanthurus|atri|surgeon', Chases_during_observation, ignore.case = TRUE)~"yes",
                                            TRUE~"no"))%>%
    relocate(Surgeonfish_binary_chases, .after = Binary_chases)
behav_dat_w_site

behav_dat_w_site%>%
  filter(Stegastes_binary_chases=="yes") #19

behav_dat_w_site%>%
  filter(Binary_chases=="Yes") #33


behav_dat_w_site%>%
  filter(Surgeonfish_binary_chases=="yes") #18

behav_dat_w_site%>%
  filter(Surgeonfish_binary_chases=="yes"&Stegastes_binary_chases=="yes") #4

#so 33 total fish were chased at least once, of which 19 were by stegastes, 18 were by surgeonfish, including 4 individuals chased by both.

18+19-4 #33....that accounts for all chases** Looks like maybe one chase by parrotfish, but also chased by other surgeonfish so can ignore. 

```


#check sample sizes by site, center predictors for analyses
```{r}
behav_dat_w_site%>%
  group_by(site)%>%
  summarize(n_site = length(total_bites_per_minute))


behav_dat_w_site_c<-
  behav_dat_w_site%>%
  mutate(N15_c = base::scale(N15, center = TRUE, scale = FALSE),
          mean_atri_biomass_c = base::scale(mean_atri_biomass, center = TRUE, scale = FALSE),
           mean_predator_biomass_c = base::scale(mean_predator_biomass, center = TRUE, scale = FALSE),
          mean_damsel_biomass_c = base::scale(mean_damsel_biomass, center = TRUE, scale = FALSE),
         mean_turf_obs_adjusted_c = base::scale(mean_turf_obs_adjusted, center = TRUE, scale = FALSE),
         mean_structure_c =  base::scale(mean_structure, center = TRUE, scale = FALSE),
         mean_seabird_n_input_c =  base::scale(mean_seabird_n_input, center = TRUE, scale = FALSE),
         wave_c = base::scale(wave_energy_manual, center = TRUE, scale = FALSE),
         time_hours_c = base::scale(time_hours, center = TRUE, scale = FALSE),
         log_wave = log(wave_energy_manual),
         log_wave_c = base::scale(log_wave, center = TRUE, scale = FALSE))%>%
  mutate(log_total_bites_per_minute = log(total_bites_per_minute))

  
```

###----------------dag-based analyses----------------


#effect of n15 on total bites per minute: -----
```{r, warning = FALSE, message = FALSE, results = FALSE, fig.show='hide'}

#two possible adjustment sets: 

###Run models TOTAL EFFECT--------
##only option - updated DAG----
total_bites_n15_mod_site_loglink_option3 <-
  brm(total_bites_per_minute ~ N15_c   + log_wave_c +  (1|site),
                data=behav_dat_w_site_c, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_bites_n15_mod_site_loglink_option3") #worked
print(total_bites_n15_mod_site_loglink_option3)

plot(total_bites_n15_mod_site_loglink_option3, ask = FALSE)
pp_check(total_bites_n15_mod_site_loglink_option3)
#looks good

hypothesis(total_bites_n15_mod_site_loglink_option3, "N15_c<0") #1 - so still strong negative effect**

total_bites_n15_mod_site_loglink_option3%>%
  spread_draws(b_N15_c)%>%
  median_hdi(exp(b_N15_c))
#0.8049985	0.7054017	0.9061607		- nearly identical to above

1-0.8049985 #0.1950015
1-0.7054017 #0.2945983
1-0.9061607 #0.0938393

```


###compare to other potential causes of behavior: 
```{r}

#####Aggressive encounters----------------
total_and_direct_bites_mod_site_loglink_aggression <-
  brm(total_bites_per_minute ~ Binary_chases + mean_atri_biomass_c + mean_damsel_biomass_c  +  (1|site),
                data=behav_dat_w_site_c, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_and_direct_bites_mod_site_loglink_aggression") #worked
print(total_and_direct_bites_mod_site_loglink_aggression)

plot(total_and_direct_bites_mod_site_loglink_aggression, ask = FALSE)
pp_check(total_and_direct_bites_mod_site_loglink_aggression)
#looks good

hypothesis(total_and_direct_bites_mod_site_loglink_aggression, "Binary_chasesYes<0") #0.32 - no effect

total_and_direct_bites_mod_site_loglink_aggression%>%
  spread_draws(b_Binary_chasesYes)%>%
  median_hdi(exp(b_Binary_chasesYes))
#1.07507	0.7861949	1.426391	



#####A tri biomass----------------
total_bites_mod_site_loglink_atribio <-
  brm(total_bites_per_minute ~ mean_atri_biomass_c +  N15_c + mean_predator_biomass_c + mean_structure_c  + mean_turf_obs_adjusted_c +  (1|site),
                data=behav_dat_w_site_c, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_bites_mod_site_loglink_atribio") #2 divergent
print(total_bites_mod_site_loglink_atribio)

plot(total_bites_mod_site_loglink_atribio, ask = FALSE)
pp_check(total_bites_mod_site_loglink_atribio)
#looks good

hypothesis(total_bites_mod_site_loglink_atribio, "mean_atri_biomass_c>0") #0.58 - no real effect

total_bites_mod_site_loglink_atribio%>%
  spread_draws(b_mean_atri_biomass_c)%>%
  median_hdi(exp(b_mean_atri_biomass_c))
#1.003175	0.9482985	1.057293	


####Damselfish----------------
total_bites_mod_site_loglink_damsel <-
  brm(total_bites_per_minute ~ mean_damsel_biomass_c + mean_predator_biomass_c + mean_structure_c  +  (1|site),
                data=behav_dat_w_site_c, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_bites_mod_site_loglink_damsel") #worked
print(total_bites_mod_site_loglink_damsel)

plot(total_bites_mod_site_loglink_damsel, ask = FALSE)
pp_check(total_bites_mod_site_loglink_damsel)
#looks good

hypothesis(total_bites_mod_site_loglink_damsel, "mean_damsel_biomass_c<0") #0..51 - no effect

total_bites_mod_site_loglink_damsel%>%
  spread_draws(b_mean_damsel_biomass_c)%>%
  median_hdi(exp(b_mean_damsel_biomass_c))
#0.999873	0.9859193	1.014542	


####---------Predators---------
total_bites_mod_site_loglink_pred <-
  brm(total_bites_per_minute ~ mean_predator_biomass_c + mean_structure_c  +  (1|site),
                data=behav_dat_w_site_c, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_bites_mod_site_loglink_pred") #worked
print(total_bites_mod_site_loglink_pred)

plot(total_bites_mod_site_loglink_pred, ask = FALSE)
pp_check(total_bites_mod_site_loglink_pred)
#looks good

hypothesis(total_bites_mod_site_loglink_pred, "mean_predator_biomass_c<0") #0.03 - SO POSITIVE EFFECT OF PREDATOR BIOMASS ON BITE RATE***

total_bites_mod_site_loglink_pred%>%
  spread_draws(b_mean_predator_biomass_c)%>%
  median_hdi(exp(b_mean_predator_biomass_c))
#1.035049	0.9962155	1.071328	



####---------Structure---------
total_bites_mod_site_loglink_struct <-
  brm(total_bites_per_minute ~ mean_structure_c  + log_wave_c +  (1|site),
                data=behav_dat_w_site_c, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_bites_mod_site_loglink_struct") #worked
print(total_bites_mod_site_loglink_struct)

plot(total_bites_mod_site_loglink_struct, ask = FALSE)
pp_check(total_bites_mod_site_loglink_struct)
#looks good

hypothesis(total_bites_mod_site_loglink_struct, "mean_structure_c<0") #.3

total_bites_mod_site_loglink_struct%>%
  spread_draws(b_mean_structure_c)%>%
  median_hdi(exp(b_mean_structure_c))
#	1.305715	0.1553781	3.563813	




####---------Time of day---------
total_direct_bites_mod_site_loglink_time <-
  brm(total_bites_per_minute ~ time_hours_c   +  (1|site),
                data=behav_dat_w_site_c, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_direct_bites_mod_site_loglink_time") #worked
print(total_direct_bites_mod_site_loglink_time)

plot(total_direct_bites_mod_site_loglink_time, ask = FALSE)
pp_check(total_direct_bites_mod_site_loglink_time)
#looks good

hypothesis(total_direct_bites_mod_site_loglink_time, "time_hours_c<0") #0.38

total_direct_bites_mod_site_loglink_time%>%
  spread_draws(b_time_hours_c)%>%
  median_hdi(exp(b_time_hours_c))
#	1.026659	0.8741239	1.192952




####---------Turf cover---------
total_bites_mod_site_loglink_turf <-
  brm(total_bites_per_minute ~ mean_turf_obs_adjusted_c   +  mean_damsel_biomass_c  + N15_c + mean_structure_c + (1|site),
                data=behav_dat_w_site_c, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_bites_mod_site_loglink_turf") #worked
print(total_bites_mod_site_loglink_turf)

plot(total_bites_mod_site_loglink_turf, ask = FALSE)
pp_check(total_bites_mod_site_loglink_turf)
#looks good

hypothesis(total_bites_mod_site_loglink_turf, "mean_turf_obs_adjusted_c<0") #.49

total_bites_mod_site_loglink_turf%>%
  spread_draws(b_mean_turf_obs_adjusted_c)%>%
  median_hdi(exp(b_mean_turf_obs_adjusted_c))
#1.000462	0.9455902	1.062569	



####---------individual size---------
behav_dat_w_site_c_size<-
  behav_dat_w_site_c%>%
   mutate(TL_cm_c = base::scale(Size, center = TRUE, scale = FALSE))


total_bites_mod_site_loglink_size <-
  brm(total_bites_per_minute ~ TL_cm_c + (1|site),
                data=behav_dat_w_site_c_size, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_bites_mod_site_loglink_size") #worked
print(total_bites_mod_site_loglink_size)

hypothesis(total_bites_mod_site_loglink_size, "TL_cm_c>0") #0.96

total_bites_mod_site_loglink_size%>%
  spread_draws(b_TL_cm_c)%>%
  median_hdi(exp(b_TL_cm_c))
#1.087735	0.9820163	1.18776	


```


####repeat with all other behavior variables-----------
```{r}
#use: sum_distance_between_forays_per_minute  - this is the total distance travelled between forays, but scaled per minute so time doesn't matter.
#goes to 0....so add 1

##add log column to dataframes:
behav_dat_w_site_c_dist<-
  behav_dat_w_site_c%>%
  mutate(sum_dist_foray_min_plus1 = sum_distance_between_forays_per_minute+1,
         mean_dist_foray_min_plus1 = mean_distance_between_forays+1,
         distance_end_start = as.numeric(Distance_end_start_m_formatted),
        distance_end_start_plus1 = distance_end_start+1 )

```



###effect of n15 on total sumdist per minute ------------
```{r, message=FALSE}

###Run models TOTAL EFFECT--------
##only option - updated DAG----
total_sumdist_n15_mod_site_loglink_option3 <-
  brm(sum_dist_foray_min_plus1 ~ N15_c + log_wave_c +  (1|site),
                data=behav_dat_w_site_c_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_sumdist_n15_mod_site_loglink_option3") #worked
print(total_sumdist_n15_mod_site_loglink_option3)

plot(total_sumdist_n15_mod_site_loglink_option3, ask = FALSE)
pp_check(total_sumdist_n15_mod_site_loglink_option3)
#looks good

hypothesis(total_sumdist_n15_mod_site_loglink_option3, "N15_c<0") #.99 - so still strong negative effect**

total_sumdist_n15_mod_site_loglink_option3%>%
  spread_draws(b_N15_c)%>%
  median_hdi(exp(b_N15_c))
#0.8963969	0.8156484	0.9803205	

1-0.8920339 #0.1079661
1-0.8115217 #0.1884783
1-0.9721629 #0.0278371

```


###compare to other potential causes of behavior: 
```{r, message=FALSE}

#####Aggressive encounters----------------
total_and_direct_sumdist_mod_site_loglink_aggression <-
  brm(sum_dist_foray_min_plus1 ~ Binary_chases + mean_atri_biomass_c + mean_damsel_biomass_c  +  (1|site),
                data=behav_dat_w_site_c_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_and_direct_sumdist_mod_site_loglink_aggression") #worked
print(total_and_direct_sumdist_mod_site_loglink_aggression)

plot(total_and_direct_sumdist_mod_site_loglink_aggression, ask = FALSE)
pp_check(total_and_direct_sumdist_mod_site_loglink_aggression)
#looks good

hypothesis(total_and_direct_sumdist_mod_site_loglink_aggression, "Binary_chasesYes<0") 

total_and_direct_sumdist_mod_site_loglink_aggression%>%
  spread_draws(b_Binary_chasesYes)%>%
  median_hdi(exp(b_Binary_chasesYes))



#####A tri biomass----------------
total_sumdist_mod_site_loglink_atribio <-
  brm(sum_dist_foray_min_plus1 ~ mean_atri_biomass_c +  N15_c + mean_predator_biomass_c + mean_structure_c  + mean_turf_obs_adjusted_c +  (1|site),
                data=behav_dat_w_site_c_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_sumdist_mod_site_loglink_atribio") #2 divergent
print(total_sumdist_mod_site_loglink_atribio)

plot(total_sumdist_mod_site_loglink_atribio, ask = FALSE)
pp_check(total_sumdist_mod_site_loglink_atribio)
#looks good

hypothesis(total_sumdist_mod_site_loglink_atribio, "mean_atri_biomass_c<0") 

total_sumdist_mod_site_loglink_atribio%>%
  spread_draws(b_mean_atri_biomass_c)%>%
  median_hdci(exp(b_mean_atri_biomass_c))



####Damselfish----------------
total_sumdist_mod_site_loglink_damsel <-
  brm(sum_dist_foray_min_plus1 ~ mean_damsel_biomass_c + mean_predator_biomass_c + mean_structure_c  +  (1|site),
                data=behav_dat_w_site_c_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_sumdist_mod_site_loglink_damsel") #worked
print(total_sumdist_mod_site_loglink_damsel)

plot(total_sumdist_mod_site_loglink_damsel, ask = FALSE)
pp_check(total_sumdist_mod_site_loglink_damsel)
#looks good

hypothesis(total_sumdist_mod_site_loglink_damsel, "mean_damsel_biomass_c<0")  

total_sumdist_mod_site_loglink_damsel%>%
  spread_draws(b_mean_damsel_biomass_c)%>%
  median_hdi(exp(b_mean_damsel_biomass_c))



####---------Predators---------
total_sumdist_mod_site_loglink_pred <-
  brm(sum_dist_foray_min_plus1 ~ mean_predator_biomass_c + mean_structure_c  +  (1|site),
                data=behav_dat_w_site_c_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_sumdist_mod_site_loglink_pred") #worked
print(total_sumdist_mod_site_loglink_pred)

plot(total_sumdist_mod_site_loglink_pred, ask = FALSE)
pp_check(total_sumdist_mod_site_loglink_pred)
#looks good

hypothesis(total_sumdist_mod_site_loglink_pred, "mean_predator_biomass_c<0") #0.09 - SO POSITIVE EFFECT OF PREDATOR BIOMASS ON DISTANCE TRAVELLED
#travelling MORE distance with more predators. 

total_sumdist_mod_site_loglink_pred%>%
  spread_draws(b_mean_predator_biomass_c)%>%
  median_hdi(exp(b_mean_predator_biomass_c))



####---------Structure---------
total_sumdist_mod_site_loglink_struct <-
  brm(sum_dist_foray_min_plus1 ~ mean_structure_c  + log_wave_c +  (1|site),
                data=behav_dat_w_site_c_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_sumdist_mod_site_loglink_struct") #
print(total_sumdist_mod_site_loglink_struct)

plot(total_sumdist_mod_site_loglink_struct, ask = FALSE)
pp_check(total_sumdist_mod_site_loglink_struct)
#looks good

hypothesis(total_sumdist_mod_site_loglink_struct, "mean_structure_c<0") #0.29

total_sumdist_mod_site_loglink_struct%>%
  spread_draws(b_mean_structure_c)%>%
  median_hdi(exp(b_mean_structure_c))




####---------Time of day---------
total_direct_sumdist_mod_site_loglink_time <-
  brm(sum_dist_foray_min_plus1 ~ time_hours_c   +  (1|site),
                data=behav_dat_w_site_c_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_direct_sumdist_mod_site_loglink_time") #worked
print(total_direct_sumdist_mod_site_loglink_time)

plot(total_direct_sumdist_mod_site_loglink_time, ask = FALSE)
pp_check(total_direct_sumdist_mod_site_loglink_time)
#looks good

hypothesis(total_direct_sumdist_mod_site_loglink_time, "time_hours_c<0") #0.76

total_direct_sumdist_mod_site_loglink_time%>%
  spread_draws(b_time_hours_c)%>%
  median_hdi(exp(b_time_hours_c))




####---------Turf cover---------
total_sumdist_mod_site_loglink_turf <-
  brm(sum_dist_foray_min_plus1 ~ mean_turf_obs_adjusted_c   +  mean_damsel_biomass_c  + N15_c + mean_structure_c + (1|site),
                data=behav_dat_w_site_c_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_sumdist_mod_site_loglink_turf") #worked
print(total_sumdist_mod_site_loglink_turf)

plot(total_sumdist_mod_site_loglink_turf, ask = FALSE)
pp_check(total_sumdist_mod_site_loglink_turf)
#looks good

hypothesis(total_sumdist_mod_site_loglink_turf, "mean_turf_obs_adjusted_c<0") #0.58

total_sumdist_mod_site_loglink_turf%>%
  spread_draws(b_mean_turf_obs_adjusted_c)%>%
  median_hdi(exp(b_mean_turf_obs_adjusted_c))
#0.997109	0.961206	1.042732	



####---------individual size---------
behav_dat_w_site_c_dist_size<-
  behav_dat_w_site_c_dist%>%
   mutate(TL_cm_c = base::scale(Size, center = TRUE, scale = FALSE))


total_sumdist_mod_site_loglink_size <-
  brm(sum_dist_foray_min_plus1 ~ TL_cm_c + (1|site),
                data=behav_dat_w_site_c_dist_size, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_sumdist_mod_site_loglink_size") #worked
print(total_sumdist_mod_site_loglink_size)

hypothesis(total_sumdist_mod_site_loglink_size, "TL_cm_c>0") #0.45

total_sumdist_mod_site_loglink_size%>%
  spread_draws(b_TL_cm_c)%>%
  median_hdi(exp(b_TL_cm_c))

```



###run analysis - effect of n15 on mean distance per foray------------
```{r, message=FALSE}

###Run models TOTAL EFFECT-------
###NEW DAG - ONLY OPTION--------
total_meandist_n15_mod_site_loglink_option3 <-
  brm(mean_dist_foray_min_plus1 ~ N15_c + log_wave_c  +  (1|site),
                data=behav_dat_w_site_c_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_meandist_n15_mod_site_loglink_option3") #worked
print(total_meandist_n15_mod_site_loglink_option3)

plot(total_meandist_n15_mod_site_loglink_option3, ask = FALSE)
pp_check(total_meandist_n15_mod_site_loglink_option3)
#looks good

hypothesis(total_meandist_n15_mod_site_loglink_option3, "N15_c<0") #0.52

total_meandist_n15_mod_site_loglink_option3%>%
  spread_draws(b_N15_c)%>%
  median_hdi(exp(b_N15_c))
#0.9975394	0.9084294	1.09054	

1-0.9975394 #0.0101571
1-0.9084294 # 0.0999606
1-1.09054 #-0.080559

```




###compare to other potential causes of behavior: Mean dist
```{r, message=FALSE}

#####Aggressive encounters----------------
total_and_direct_meandist_mod_site_loglink_aggression <-
  brm(mean_dist_foray_min_plus1 ~ Binary_chases + mean_atri_biomass_c + mean_damsel_biomass_c  +  (1|site),
                data=behav_dat_w_site_c_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_and_direct_meandist_mod_site_loglink_aggression") #worked
print(total_and_direct_meandist_mod_site_loglink_aggression)

plot(total_and_direct_meandist_mod_site_loglink_aggression, ask = FALSE)
pp_check(total_and_direct_meandist_mod_site_loglink_aggression)
#looks good

hypothesis(total_and_direct_meandist_mod_site_loglink_aggression, "Binary_chasesYes<0")

total_and_direct_meandist_mod_site_loglink_aggression%>%
  spread_draws(b_Binary_chasesYes)%>%
  median_hdi(exp(b_Binary_chasesYes))



#####A tri biomass----------------
total_meandist_mod_site_loglink_atribio <-
  brm(mean_dist_foray_min_plus1 ~ mean_atri_biomass_c +  N15_c + mean_predator_biomass_c + mean_structure_c  + mean_turf_obs_adjusted_c +  (1|site),
                data=behav_dat_w_site_c_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_meandist_mod_site_loglink_atribio") 
print(total_meandist_mod_site_loglink_atribio)

plot(total_meandist_mod_site_loglink_atribio, ask = FALSE)
pp_check(total_meandist_mod_site_loglink_atribio)
#looks good

hypothesis(total_meandist_mod_site_loglink_atribio, "mean_atri_biomass_c<0") 

total_meandist_mod_site_loglink_atribio%>%
  spread_draws(b_mean_atri_biomass_c)%>%
  median_hdi(exp(b_mean_atri_biomass_c))



####Damselfish----------------
total_meandist_mod_site_loglink_damsel <-
  brm(mean_dist_foray_min_plus1 ~ mean_damsel_biomass_c + mean_predator_biomass_c + mean_structure_c  +  (1|site),
                data=behav_dat_w_site_c_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_meandist_mod_site_loglink_damsel") #worked
print(total_meandist_mod_site_loglink_damsel)

plot(total_meandist_mod_site_loglink_damsel, ask = FALSE)
pp_check(total_meandist_mod_site_loglink_damsel)
#looks good

hypothesis(total_meandist_mod_site_loglink_damsel, "mean_damsel_biomass_c<0") 

total_meandist_mod_site_loglink_damsel%>%
  spread_draws(b_mean_damsel_biomass_c)%>%
  median_hdi(exp(b_mean_damsel_biomass_c))



####---------Predators---------
total_meandist_mod_site_loglink_pred <-
  brm(mean_dist_foray_min_plus1 ~ mean_predator_biomass_c + mean_structure_c  +  (1|site),
                data=behav_dat_w_site_c_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_meandist_mod_site_loglink_pred") #worked
print(total_meandist_mod_site_loglink_pred)

plot(total_meandist_mod_site_loglink_pred, ask = FALSE)
pp_check(total_meandist_mod_site_loglink_pred)
#looks good

hypothesis(total_meandist_mod_site_loglink_pred, "mean_predator_biomass_c<0") 

total_meandist_mod_site_loglink_pred%>%
  spread_draws(b_mean_predator_biomass_c)%>%
  median_hdi(exp(b_mean_predator_biomass_c))


####---------Structure---------
total_meandist_mod_site_loglink_struct <-
  brm(mean_dist_foray_min_plus1 ~ mean_structure_c  + log_wave_c +  (1|site),
                data=behav_dat_w_site_c_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_meandist_mod_site_loglink_struct") #worked
print(total_meandist_mod_site_loglink_struct)

plot(total_meandist_mod_site_loglink_struct, ask = FALSE)
pp_check(total_meandist_mod_site_loglink_struct)
#looks good

hypothesis(total_meandist_mod_site_loglink_struct, "mean_structure_c<0") 

total_meandist_mod_site_loglink_struct%>%
  spread_draws(b_mean_structure_c)%>%
  median_hdi(exp(b_mean_structure_c))




####---------Time of day---------
total_direct_meandist_mod_site_loglink_time <-
  brm(mean_dist_foray_min_plus1 ~ time_hours_c   +  (1|site),
                data=behav_dat_w_site_c_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_direct_meandist_mod_site_loglink_time") #worked
print(total_direct_meandist_mod_site_loglink_time)

plot(total_direct_meandist_mod_site_loglink_time, ask = FALSE)
pp_check(total_direct_meandist_mod_site_loglink_time)
#looks good

hypothesis(total_direct_meandist_mod_site_loglink_time, "time_hours_c<0") 

total_direct_meandist_mod_site_loglink_time%>%
  spread_draws(b_time_hours_c)%>%
  median_hdi(exp(b_time_hours_c))



####---------Turf cover---------
total_meandist_mod_site_loglink_turf <-
  brm(mean_dist_foray_min_plus1 ~ mean_turf_obs_adjusted_c   +  mean_damsel_biomass_c  + N15_c + mean_structure_c + (1|site),
                data=behav_dat_w_site_c_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_meandist_mod_site_loglink_turf") #worked
print(total_meandist_mod_site_loglink_turf)

plot(total_meandist_mod_site_loglink_turf, ask = FALSE)
pp_check(total_meandist_mod_site_loglink_turf)
#looks good

hypothesis(total_meandist_mod_site_loglink_turf, "mean_turf_obs_adjusted_c<0") 

total_meandist_mod_site_loglink_turf%>%
  spread_draws(b_mean_turf_obs_adjusted_c)%>%
  median_hdi(exp(b_mean_turf_obs_adjusted_c))


####---------individual size---------

total_meandist_mod_site_loglink_size <-
  brm(mean_dist_foray_min_plus1 ~ TL_cm_c + (1|site),
                data=behav_dat_w_site_c_dist_size, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_meandist_mod_site_loglink_size") #worked
print(total_meandist_mod_site_loglink_size)

hypothesis(total_meandist_mod_site_loglink_size, "TL_cm_c>0") #

total_meandist_mod_site_loglink_size%>%
  spread_draws(b_TL_cm_c)%>%
  median_hdi(exp(b_TL_cm_c))

```



###------number of feeding bouts------

##n15 effects on feeding bouts per minute
```{r, message=FALSE}

#NEED TO SCALE BY MINUTE*****
behav_dat_w_site_c_dist_foray<-
  behav_dat_w_site_c_dist%>%
  mutate(forays_per_minute = number_forays/(total_time_seconds_numeric/60))

###Run models--------
###NEW DAG - NEED TO USE THIS-----------
total_forays_n15_mod_site_loglink_option3 <-
  brm(forays_per_minute ~ N15_c + log_wave_c +  (1|site),
                data=behav_dat_w_site_c_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_forays_n15_mod_site_loglink_option3") #worked
print(total_forays_n15_mod_site_loglink_option3)

plot(total_forays_n15_mod_site_loglink_option3, ask = FALSE)
pp_check(total_forays_n15_mod_site_loglink_option3)
#looks good

hypothesis(total_forays_n15_mod_site_loglink_option3, "N15_c<0") #1

total_forays_n15_mod_site_loglink_option3%>%
  spread_draws(b_N15_c)%>%
  median_hdi(exp(b_N15_c))
#0.8722802	0.791626	0.9531124	

1-0.8722802 # 0.1277198
1-0.791626 # 0.208374
1-0.9531124 #0.0468876

```



###compare to other potential causes of behavior: # of forays
```{r, message=FALSE}

#####Aggressive encounters----------------
total_and_direct_forays_mod_site_loglink_aggression <-
  brm(forays_per_minute ~ Binary_chases + mean_atri_biomass_c + mean_damsel_biomass_c  +  (1|site),
                data=behav_dat_w_site_c_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_and_direct_forays_mod_site_loglink_aggression") #worked
print(total_and_direct_forays_mod_site_loglink_aggression)

plot(total_and_direct_forays_mod_site_loglink_aggression, ask = FALSE)
pp_check(total_and_direct_forays_mod_site_loglink_aggression)
#looks good

hypothesis(total_and_direct_forays_mod_site_loglink_aggression, "Binary_chasesYes<0") 

total_and_direct_forays_mod_site_loglink_aggression%>%
  spread_draws(b_Binary_chasesYes)%>%
  median_hdi(exp(b_Binary_chasesYes))



#####A tri biomass----------------
total_forays_mod_site_loglink_atribio <-
  brm(forays_per_minute ~ mean_atri_biomass_c +  N15_c + mean_predator_biomass_c + mean_structure_c  + mean_turf_obs_adjusted_c +  (1|site),
                data=behav_dat_w_site_c_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_forays_mod_site_loglink_atribio") #2 divergent
print(total_forays_mod_site_loglink_atribio)

plot(total_forays_mod_site_loglink_atribio, ask = FALSE)
pp_check(total_forays_mod_site_loglink_atribio)
#looks good

hypothesis(total_forays_mod_site_loglink_atribio, "mean_atri_biomass_c<0") 

total_forays_mod_site_loglink_atribio%>%
  spread_draws(b_mean_atri_biomass_c)%>%
  median_hdi(exp(b_mean_atri_biomass_c))


####Damselfish----------------
total_forays_mod_site_loglink_damsel <-
  brm(forays_per_minute ~ mean_damsel_biomass_c + mean_predator_biomass_c + mean_structure_c  +  (1|site),
                data=behav_dat_w_site_c_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_forays_mod_site_loglink_damsel") #worked
print(total_forays_mod_site_loglink_damsel)

plot(total_forays_mod_site_loglink_damsel, ask = FALSE)
pp_check(total_forays_mod_site_loglink_damsel)
#looks good

hypothesis(total_forays_mod_site_loglink_damsel, "mean_damsel_biomass_c<0") 

total_forays_mod_site_loglink_damsel%>%
  spread_draws(b_mean_damsel_biomass_c)%>%
  median_hdi(exp(b_mean_damsel_biomass_c))



####---------Predators---------
total_forays_mod_site_loglink_pred <-
  brm(forays_per_minute ~ mean_predator_biomass_c + mean_structure_c  +  (1|site),
                data=behav_dat_w_site_c_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_forays_mod_site_loglink_pred") #worked
print(total_forays_mod_site_loglink_pred)

plot(total_forays_mod_site_loglink_pred, ask = FALSE)
pp_check(total_forays_mod_site_loglink_pred)
#looks good

hypothesis(total_forays_mod_site_loglink_pred, "mean_predator_biomass_c<0") 

total_forays_mod_site_loglink_pred%>%
  spread_draws(b_mean_predator_biomass_c)%>%
  median_hdi(exp(b_mean_predator_biomass_c))



####---------Structure---------
total_forays_mod_site_loglink_struct <-
  brm(forays_per_minute ~ mean_structure_c  + log_wave_c +  (1|site),
                data=behav_dat_w_site_c_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_forays_mod_site_loglink_struct") #worked
print(total_forays_mod_site_loglink_struct)

plot(total_forays_mod_site_loglink_struct, ask = FALSE)
pp_check(total_forays_mod_site_loglink_struct)
#looks good

hypothesis(total_forays_mod_site_loglink_struct, "mean_structure_c<0") 

total_forays_mod_site_loglink_struct%>%
  spread_draws(b_mean_structure_c)%>%
  median_hdi(exp(b_mean_structure_c))




####---------Time of day---------
total_direct_forays_mod_site_loglink_time <-
  brm(forays_per_minute ~ time_hours_c   +  (1|site),
                data=behav_dat_w_site_c_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_direct_forays_mod_site_loglink_time") #worked
print(total_direct_forays_mod_site_loglink_time)

plot(total_direct_forays_mod_site_loglink_time, ask = FALSE)
pp_check(total_direct_forays_mod_site_loglink_time)
#looks good

hypothesis(total_direct_forays_mod_site_loglink_time, "time_hours_c<0") 

total_direct_forays_mod_site_loglink_time%>%
  spread_draws(b_time_hours_c)%>%
  median_hdi(exp(b_time_hours_c))





####---------Turf cover---------
total_forays_mod_site_loglink_turf <-
  brm(forays_per_minute ~ mean_turf_obs_adjusted_c   +  mean_damsel_biomass_c  + N15_c + mean_structure_c + (1|site),
                data=behav_dat_w_site_c_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_forays_mod_site_loglink_turf") #worked
print(total_forays_mod_site_loglink_turf)

plot(total_forays_mod_site_loglink_turf, ask = FALSE)
pp_check(total_forays_mod_site_loglink_turf)
#looks good

hypothesis(total_forays_mod_site_loglink_turf, "mean_turf_obs_adjusted_c<0") #.49

total_forays_mod_site_loglink_turf%>%
  spread_draws(b_mean_turf_obs_adjusted_c)%>%
  median_hdi(exp(b_mean_turf_obs_adjusted_c))
#1.000462	0.9455902	1.062569	


####---------individual size---------
behav_dat_w_site_c_dist_foray_size<-
  behav_dat_w_site_c_dist_foray%>%
   mutate(TL_cm_c = base::scale(Size, center = TRUE, scale = FALSE))


total_forays_mod_site_loglink_size <-
  brm(sum_dist_foray_min_plus1 ~ TL_cm_c + (1|site),
                data=behav_dat_w_site_c_dist_foray_size, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_forays_mod_site_loglink_size") #worked
print(total_forays_mod_site_loglink_size)

hypothesis(total_forays_mod_site_loglink_size, "TL_cm_c>0") 

total_forays_mod_site_loglink_size%>%
  spread_draws(b_TL_cm_c)%>%
  median_hdi(exp(b_TL_cm_c))

```



###bites per bout: mean_bites_per_foray --------

##n15 effects on mean_bites_per_foray
```{r, message=FALSE}

###Run models--------
###NEW DAG - ONLY OPTION----
total_foraybites_n15_mod_site_loglink_option3 <-
  brm(mean_bites_per_foray ~ N15_c + log_wave_c +  (1|site),
                data=behav_dat_w_site_c_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_foraybites_n15_mod_site_loglink_option3") #worked
print(total_foraybites_n15_mod_site_loglink_option3)

plot(total_foraybites_n15_mod_site_loglink_option3, ask = FALSE)
pp_check(total_foraybites_n15_mod_site_loglink_option3)
#looks good

hypothesis(total_foraybites_n15_mod_site_loglink_option3, "N15_c<0") #.98

total_foraybites_n15_mod_site_loglink_option3%>%
  spread_draws(b_N15_c)%>%
  median_hdi(exp(b_N15_c))
#0.89494	0.8188675	0.9768487	
1 -  0.89494 #0.10506
1 -  0.8188675 # 0.1811325
1 -  0.9768487 #0.0231513

```



###compare to other cuases of behavior - BITES PER FORAY
```{r, message=FALSE}

#####Aggressive encounters----------------
total_and_direct_foraybites_mod_site_loglink_aggression <-
  brm(mean_bites_per_foray ~ Binary_chases + mean_atri_biomass_c + mean_damsel_biomass_c  +  (1|site),
                data=behav_dat_w_site_c_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_and_direct_foraybites_mod_site_loglink_aggression") #worked
print(total_and_direct_foraybites_mod_site_loglink_aggression)

plot(total_and_direct_foraybites_mod_site_loglink_aggression, ask = FALSE)
pp_check(total_and_direct_foraybites_mod_site_loglink_aggression)
#looks good

hypothesis(total_and_direct_foraybites_mod_site_loglink_aggression, "Binary_chasesYes<0") 

total_and_direct_foraybites_mod_site_loglink_aggression%>%
  spread_draws(b_Binary_chasesYes)%>%
  median_hdi(exp(b_Binary_chasesYes))



#####A tri biomass----------------
total_foraybites_mod_site_loglink_atribio <-
  brm(mean_bites_per_foray ~ mean_atri_biomass_c +  N15_c + mean_predator_biomass_c + mean_structure_c  + mean_turf_obs_adjusted_c +  (1|site),
                data=behav_dat_w_site_c_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_foraybites_mod_site_loglink_atribio") 
print(total_foraybites_mod_site_loglink_atribio)

plot(total_foraybites_mod_site_loglink_atribio, ask = FALSE)
pp_check(total_foraybites_mod_site_loglink_atribio)
#looks good

hypothesis(total_foraybites_mod_site_loglink_atribio, "mean_atri_biomass_c<0") 

total_foraybites_mod_site_loglink_atribio%>%
  spread_draws(b_mean_atri_biomass_c)%>%
  median_hdi(exp(b_mean_atri_biomass_c))



####Damselfish----------------
total_foraybites_mod_site_loglink_damsel <-
  brm(mean_bites_per_foray ~ mean_damsel_biomass_c + mean_predator_biomass_c + mean_structure_c  +  (1|site),
                data=behav_dat_w_site_c_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_foraybites_mod_site_loglink_damsel") #worked
print(total_foraybites_mod_site_loglink_damsel)

plot(total_foraybites_mod_site_loglink_damsel, ask = FALSE)
pp_check(total_foraybites_mod_site_loglink_damsel)
#looks good

hypothesis(total_foraybites_mod_site_loglink_damsel, "mean_damsel_biomass_c<0") 

total_foraybites_mod_site_loglink_damsel%>%
  spread_draws(b_mean_damsel_biomass_c)%>%
  median_hdi(exp(b_mean_damsel_biomass_c))



####---------Predators---------
total_foraybites_mod_site_loglink_pred <-
  brm(mean_bites_per_foray ~ mean_predator_biomass_c + mean_structure_c  +  (1|site),
                data=behav_dat_w_site_c_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_foraybites_mod_site_loglink_pred") #worked
print(total_foraybites_mod_site_loglink_pred)

plot(total_foraybites_mod_site_loglink_pred, ask = FALSE)
pp_check(total_foraybites_mod_site_loglink_pred)
#looks good

hypothesis(total_foraybites_mod_site_loglink_pred, "mean_predator_biomass_c<0") 

total_foraybites_mod_site_loglink_pred%>%
  spread_draws(b_mean_predator_biomass_c)%>%
  median_hdi(exp(b_mean_predator_biomass_c))


####---------Structure---------
total_foraybites_mod_site_loglink_struct <-
  brm(mean_bites_per_foray ~ mean_structure_c  + log_wave_c +  (1|site),
                data=behav_dat_w_site_c_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_foraybites_mod_site_loglink_struct") #worked
print(total_foraybites_mod_site_loglink_struct)

plot(total_foraybites_mod_site_loglink_struct, ask = FALSE)
pp_check(total_foraybites_mod_site_loglink_struct)
#looks good

hypothesis(total_foraybites_mod_site_loglink_struct, "mean_structure_c<0") #

total_foraybites_mod_site_loglink_struct%>%
  spread_draws(b_mean_structure_c)%>%
  median_hdi(exp(b_mean_structure_c))



####---------Time of day---------
total_direct_foraybites_mod_site_loglink_time <-
  brm(mean_bites_per_foray ~ time_hours_c   +  (1|site),
                data=behav_dat_w_site_c_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_direct_foraybites_mod_site_loglink_time") #worked
print(total_direct_foraybites_mod_site_loglink_time)

plot(total_direct_foraybites_mod_site_loglink_time, ask = FALSE)
pp_check(total_direct_foraybites_mod_site_loglink_time)
#looks good

hypothesis(total_direct_foraybites_mod_site_loglink_time, "time_hours_c<0") #

total_direct_foraybites_mod_site_loglink_time%>%
  spread_draws(b_time_hours_c)%>%
  median_hdi(exp(b_time_hours_c))




####---------Turf cover---------
total_foraybites_mod_site_loglink_turf <-
  brm(mean_bites_per_foray ~ mean_turf_obs_adjusted_c   +  mean_damsel_biomass_c  + N15_c + mean_structure_c + (1|site),
                data=behav_dat_w_site_c_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_foraybites_mod_site_loglink_turf") #worked
print(total_foraybites_mod_site_loglink_turf)

plot(total_foraybites_mod_site_loglink_turf, ask = FALSE)
pp_check(total_foraybites_mod_site_loglink_turf)
#looks good

hypothesis(total_foraybites_mod_site_loglink_turf, "mean_turf_obs_adjusted_c<0") #

total_foraybites_mod_site_loglink_turf%>%
  spread_draws(b_mean_turf_obs_adjusted_c)%>%
  median_hdi(exp(b_mean_turf_obs_adjusted_c))



####---------individual size---------
total_foraybites_mod_site_loglink_size <-
  brm(mean_bites_per_foray ~ TL_cm_c + (1|site),
                data=behav_dat_w_site_c_dist_foray_size, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_foraybites_mod_site_loglink_size") #worked
print(total_foraybites_mod_site_loglink_size)

hypothesis(total_foraybites_mod_site_loglink_size, "TL_cm_c>0") #

total_foraybites_mod_site_loglink_size%>%
  spread_draws(b_TL_cm_c)%>%
  median_hdi(exp(b_TL_cm_c))

```


#----------------PLOTS ----------------------

###let's plot these: n15------

###total bites plots--------
```{r}
bites_dag_me<-conditional_effects(total_bites_n15_mod_site_loglink_option3, effects = "N15_c", plot = FALSE)[[1]]

mean(behav_dat_w_site_c_dist$N15)

bites_dag_me_unscale<-
  bites_dag_me%>%
  mutate(N15 = N15_c +2.834105)


bites_draws<-
behav_dat_w_site_c %>%
  data_grid(N15_c = seq_range(N15_c, n = 50),
            log_wave_c = 0) %>%
  add_epred_draws(total_bites_n15_mod_site_loglink_option3, ndraws = 500, re_formula = NA)


bites_draws_rescale<-
  bites_draws%>%
  mutate(N15 = N15_c +2.834105)


bites_draw_plot<-
behav_dat_w_site_c%>%
  ggplot(aes(x = N15, y = total_bites_per_minute))+
  geom_line(data = bites_draws_rescale, aes(y = .epred, x = N15, group = .draw), color = "grey", alpha = .2, lwd = .5) +
    #ylab(expression(Surgeonfish~italic(delta)^15*N)) +
    # xlab(expression(Seabird~breeding~biomass~(kg~ha^-1))) +
     geom_line(data = bites_dag_me_unscale, aes(y = estimate__), alpha = .9, lwd = 1) +
   geom_point(color = "#d0e2af", fill = "#d0e2af", size = 3, alpha = .8)+
    # geom_point(color = "#f5db99", fill = "#f5db99", size = 4, alpha = .8)+
     xlab(expression(Turf~italic(delta)^15*N)) +
  ylab("Bites per minute")+
  theme_bw() +
   theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.title = element_blank(),
        legend.direction = "horizontal",
       #legend.position = "none"#,
        legend.position = "inside",
        legend.position.inside = c(.8, .8)
       )
bites_draw_plot
###

###posterior plot:
bites_plot_post_dist<-
ggplot() +
   geom_vline(xintercept=1, lty=2, alpha = .5)+
  stat_halfeye(data = as_draws_df(total_bites_n15_mod_site_loglink_option3), aes(x = exp(b_N15_c),  y = 1, fill =  after_stat(x< 1)), 
               point_interval=median_hdi, .width=c(.9,.8),  slab_alpha = .9) + 
#scale_fill_manual(values = c("#0072B2", "#D55E00"	))+
 scale_fill_manual(values = c( "lightgrey", "#d0e2af"))+
 theme_minimal()+
   ylab("")+
   # xlab(expression(Effect~of~surgeonfish~italic(delta)^15*N~on~growth)) +
   xlab("")+
 # xlim(c(-1,2))+
 #  xlab("")+
  theme_bw()+
   theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(), 
        axis.ticks.y =  element_blank(), 
        axis.text.y =  element_blank(), 
        legend.position = "none",  
        rect = element_rect(fill = "transparent"),  
        plot.background = element_rect(fill = "transparent", color = NA),
        text=element_text(size=12)) #,  family="sans"
bites_plot_post_dist

```


####total distance travelled Plots (total effect)------
```{r}
dist_dag_me<-conditional_effects(total_sumdist_n15_mod_site_loglink_option3, effects = "N15_c", plot = FALSE)[[1]]

mean(behav_dat_w_site_c_dist$N15)

dist_dag_me_unscale<-
  dist_dag_me%>%
  mutate(N15 = N15_c +2.834105)


dist_draws<-
behav_dat_w_site_c_dist %>%
  data_grid(N15_c = seq_range(N15_c, n = 50),
             log_wave_c = 0) %>%
  add_epred_draws(total_sumdist_n15_mod_site_loglink_option3, ndraws = 500, re_formula = NA)

dist_draws_rescale<-
  dist_draws%>%
  mutate(N15 = N15_c +2.834105)


dist_draw_plot<-
behav_dat_w_site_c_dist%>%
  ggplot(aes(x = N15, y = sum_dist_foray_min_plus1))+
  geom_line(data = dist_draws_rescale, aes(y = .epred, x = N15, group = .draw), color = "grey", alpha = .2, lwd = .5) +
    #ylab(expression(Surgeonfish~italic(delta)^15*N)) +
    # xlab(expression(Seabird~breeding~biomass~(kg~ha^-1))) +
     geom_line(data = dist_dag_me_unscale, aes(y = estimate__), alpha = .9, lwd = 1) +
       geom_point(color = "#d0e2af", fill = "#d0e2af", size = 3, alpha = .8)+
    # geom_point(color = "#f5db99", fill = "#f5db99", size = 4, alpha = .8)+
     xlab(expression(Turf~italic(delta)^15*N)) +
  ylab("Distance travelled (m) per minute")+
    scale_y_continuous(breaks = c(1, 3.5, 6, 8.5, 11, 13.5), labels = c(0, 2.5, 5, 7.5, 10, 12.5)) +#because added 1 for log - reduce all by 1 #limits = c(.1,13.5), 
  theme_bw() +
   theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.title = element_blank(),
        legend.direction = "horizontal",
       #legend.position = "none"#,
        legend.position = "inside",
        legend.position.inside = c(.8, .8)
       )
dist_draw_plot

###posterior plot:
dist_plot_post_dist<-
ggplot() +
   geom_vline(xintercept=1, lty=2, alpha = .5)+
  stat_halfeye(data = as_draws_df(total_sumdist_n15_mod_site_loglink_option3), aes(x = exp(b_N15_c),  y = 1, fill =  after_stat(x< 1)), 
               point_interval=median_hdi, .width=c(.9,.8),  slab_alpha = .9) + 
#scale_fill_manual(values = c("#0072B2", "#D55E00"	))+
 scale_fill_manual(values = c( "lightgrey", "#d0e2af"))+
 theme_minimal()+
   ylab("")+
   # xlab(expression(Effect~of~surgeonfish~italic(delta)^15*N~on~growth)) +
   xlab("")+
 scale_x_continuous(breaks = c(0.8, 0.9, 1.0))+
 #  xlab("")+
  theme_bw()+
   theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(), 
        axis.ticks.y =  element_blank(), 
        axis.text.y =  element_blank(), 
        legend.position = "none",  
        rect = element_rect(fill = "transparent"),  
        plot.background = element_rect(fill = "transparent", color = NA),
        text=element_text(size=12)) #,  family="sans"
dist_plot_post_dist

```


####mean distance travelled Plots------
```{r}
mdist_dag_me<-conditional_effects(total_meandist_n15_mod_site_loglink_option3, effects = "N15_c", plot = FALSE)[[1]]

mean(behav_dat_w_site_c_dist$N15)

mdist_dag_me_unscale<-
  mdist_dag_me%>%
  mutate(N15 = N15_c +2.834105)


mdist_draws<-
behav_dat_w_site_c_dist %>%
  data_grid(N15_c = seq_range(N15_c, n = 50),
            log_wave_c = 0) %>%
  add_epred_draws(total_meandist_n15_mod_site_loglink_option3, ndraws = 500, re_formula = NA)


mdist_draws_rescale<-
  mdist_draws%>%
  mutate(N15 = N15_c +2.834105)


mdist_draw_plot<-
behav_dat_w_site_c_dist%>%
  ggplot(aes(x = N15, y = mean_dist_foray_min_plus1))+
  geom_line(data = mdist_draws_rescale, aes(y = .epred, x = N15, group = .draw), color = "grey", alpha = .2, lwd = .5) +
    #ylab(expression(Surgeonfish~italic(delta)^15*N)) +
    # xlab(expression(Seabird~breeding~biomass~(kg~ha^-1))) +
     geom_line(data = mdist_dag_me_unscale, aes(y = estimate__), alpha = .9, lwd = 1) +
  #   geom_point(aes(color = site, fill = site), size = 4, alpha = .8)+
   geom_point(color = "#d0e2af", fill = "#d0e2af", size = 3, alpha = .8)+
    # geom_point(color = "#f5db99", fill = "#f5db99", size = 4, alpha = .8)+
     xlab(expression(Turf~italic(delta)^15*N)) +
  ylab("Distance travelled (m) per foray")+
    scale_y_continuous(breaks = c(1, 3.5, 6, 8.5, 11, 13.5, 16.0), labels = c(0, 2.5, 5, 7.5, 10, 12.5, 15.0)) +#because added 1 for log - reduce all by 1
  theme_bw() +
   theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.title = element_blank(),
        legend.direction = "horizontal",
       #legend.position = "none"#,
        legend.position = "inside",
        legend.position.inside = c(.8, .8)
       )
mdist_draw_plot
###

###posterior plot:
mdist_plot_post_dist<-
ggplot() +
   geom_vline(xintercept=1, lty=2, alpha = .5)+
  stat_halfeye(data = as_draws_df(total_meandist_n15_mod_site_loglink_option3), aes(x = exp(b_N15_c),  y = 1, fill =  after_stat(x< 1)), 
               point_interval=median_hdi, .width=c(.9,.8),  slab_alpha = .9) + 
#scale_fill_manual(values = c("#0072B2", "#D55E00"	))+
 scale_fill_manual(values = c( "lightgrey", "#d0e2af"))+
 theme_minimal()+
   ylab("")+
   # xlab(expression(Effect~of~surgeonfish~italic(delta)^15*N~on~growth)) +
   xlab("")+
 # xlim(c(-1,2))+
 #  xlab("")+
  theme_bw()+
   theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(), 
        axis.ticks.y =  element_blank(), 
        axis.text.y =  element_blank(), 
        legend.position = "none",  
        rect = element_rect(fill = "transparent"),  
        plot.background = element_rect(fill = "transparent", color = NA),
        text=element_text(size=12)) #,  family="sans"
mdist_plot_post_dist

```


####number of forays PER MINUTE Plots------
```{r}
foray_dag_me<-conditional_effects(total_forays_n15_mod_site_loglink_option3 , effects = "N15_c", plot = FALSE)[[1]]

mean(behav_dat_w_site_c_dist$N15)

foray_dag_me_unscale<-
  foray_dag_me%>%
  mutate(N15 = N15_c +2.834105)


foray_draws<-
behav_dat_w_site_c_dist_foray %>%
  data_grid(N15_c = seq_range(N15_c, n = 50),
             log_wave_c = 0) %>%
  add_epred_draws(total_forays_n15_mod_site_loglink_option3 , ndraws = 500, re_formula = NA)


foray_draws_rescale<-
  foray_draws%>%
  mutate(N15 = N15_c +2.834105)


foray_draw_plot<-
behav_dat_w_site_c_dist_foray%>%
  ggplot(aes(x = N15, y = forays_per_minute))+
  geom_line(data = foray_draws_rescale, aes(y = .epred, x = N15, group = .draw), color = "grey", alpha = .2, lwd = .5) +
    #ylab(expression(Surgeonfish~italic(delta)^15*N)) +
    # xlab(expression(Seabird~breeding~biomass~(kg~ha^-1))) +
     geom_line(data = foray_dag_me_unscale, aes(y = estimate__), alpha = .9, lwd = 1) +
   geom_point(color = "#d0e2af", fill = "#d0e2af", size = 3, alpha = .8)+
    # geom_point(color = "#f5db99", fill = "#f5db99", size = 4, alpha = .8)+
     xlab(expression(Turf~italic(delta)^15*N)) +
  ylab("Forays per minute")+
  theme_bw() +
   theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.title = element_blank(),
        legend.direction = "horizontal",
       #legend.position = "none"#,
        legend.position = "inside",
        legend.position.inside = c(.8, .8)
       )
foray_draw_plot
###

###posterior plot:
foray_plot_post_dist<-
ggplot() +
   geom_vline(xintercept=1, lty=2, alpha = .5)+
  stat_halfeye(data = as_draws_df(total_forays_n15_mod_site_loglink_option3), aes(x = exp(b_N15_c),  y = 1, fill =  after_stat(x< 1)), 
               point_interval=median_hdi, .width=c(.9,.8),  slab_alpha = .9) + 
#scale_fill_manual(values = c("#0072B2", "#D55E00"	))+
 scale_fill_manual(values = c( "lightgrey", "#d0e2af"))+
 theme_minimal()+
   ylab("")+
   # xlab(expression(Effect~of~surgeonfish~italic(delta)^15*N~on~growth)) +
   xlab("")+
 # xlim(c(-1,2))+
 #  xlab("")+
  theme_bw()+
   theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(), 
        axis.ticks.y =  element_blank(), 
        axis.text.y =  element_blank(), 
        legend.position = "none",  
        rect = element_rect(fill = "transparent"),  
        plot.background = element_rect(fill = "transparent", color = NA),
        text=element_text(size=12)) #,  family="sans"
foray_plot_post_dist

```

###bites per foray plots--------
```{r}
bites_foray_dag_me<-conditional_effects(total_foraybites_n15_mod_site_loglink_option3, effects = "N15_c", plot = FALSE)[[1]]

mean(behav_dat_w_site_c_dist$N15)

bites_foray_dag_me_unscale<-
  bites_foray_dag_me%>%
  mutate(N15 = N15_c +2.834105)


bites_foray_draws<-
behav_dat_w_site_c %>%
  data_grid(N15_c = seq_range(N15_c, n = 50),
             log_wave_c = 0) %>%
  add_epred_draws(total_foraybites_n15_mod_site_loglink_option3, ndraws = 500, re_formula = NA)


bites_foray_draws_rescale<-
  bites_foray_draws%>%
  mutate(N15 = N15_c +2.834105)


bites_foray_draw_plot<-
behav_dat_w_site_c%>%
  ggplot(aes(x = N15, y = mean_bites_per_foray))+
  geom_line(data = bites_foray_draws_rescale, aes(y = .epred, x = N15, group = .draw), color = "grey", alpha = .2, lwd = .5) +
    #ylab(expression(Surgeonfish~italic(delta)^15*N)) +
    # xlab(expression(Seabird~breeding~biomass~(kg~ha^-1))) +
     geom_line(data = bites_foray_dag_me_unscale, aes(y = estimate__), alpha = .9, lwd = 1) +
   geom_point(color = "#d0e2af", fill = "#d0e2af", size = 3, alpha = .8)+
    # geom_point(color = "#f5db99", fill = "#f5db99", size = 4, alpha = .8)+
     xlab(expression(Turf~italic(delta)^15*N)) +
  ylab("Bites per foray")+
  theme_bw() +
   theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.title = element_blank(),
        legend.direction = "horizontal",
       #legend.position = "none"#,
        legend.position = "inside",
        legend.position.inside = c(.8, .8)
       )
bites_foray_draw_plot
###

###posterior plot:
bites_foray_plot_post_dist<-
ggplot() +
   geom_vline(xintercept=1, lty=2, alpha = .5)+
  stat_halfeye(data = as_draws_df(total_foraybites_n15_mod_site_loglink_option3), aes(x = exp(b_N15_c),  y = 1, fill =  after_stat(x< 1)), 
               point_interval=median_hdi, .width=c(.9,.8),  slab_alpha = .9) + 
#scale_fill_manual(values = c("#0072B2", "#D55E00"	))+
 scale_fill_manual(values = c( "lightgrey", "#d0e2af"))+
 theme_minimal()+
   ylab("")+
   # xlab(expression(Effect~of~surgeonfish~italic(delta)^15*N~on~growth)) +
   xlab("")+
 # xlim(c(-1,2))+
 #  xlab("")+
  theme_bw()+
   theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(), 
        axis.ticks.y =  element_blank(), 
        axis.text.y =  element_blank(), 
        legend.position = "none",  
        rect = element_rect(fill = "transparent"),  
        plot.background = element_rect(fill = "transparent", color = NA),
        text=element_text(size=12)) #,  family="sans"
bites_foray_plot_post_dist

```

####------------combine and save plots-------
```{r}


foray_plots_c<-
  ggdraw() +
  draw_plot(foray_draw_plot) +
  draw_plot(foray_plot_post_dist, x = 0.6, y = .6, width = .35, height = .35)
foray_plots_c

bites_foray_plots_c<-
  ggdraw() +
  draw_plot(bites_foray_draw_plot) +
  draw_plot(bites_foray_plot_post_dist, x = 0.6, y = .6, width = .35, height = .35)
bites_foray_plots_c

mean_dist_plots_c<-
  ggdraw() +
  draw_plot(mdist_draw_plot) +
  draw_plot(mdist_plot_post_dist, x = 0.6, y = .6, width = .35, height = .35)
mean_dist_plots_c

tot_dist_plots_c<-
  ggdraw() +
  draw_plot(dist_draw_plot) +
  draw_plot(dist_plot_post_dist, x = 0.6, y = .6, width = .35, height = .35)
tot_dist_plots_c

bites_min_plots_c<-
  ggdraw() +
  draw_plot(bites_draw_plot) +
  draw_plot(bites_plot_post_dist, x = 0.6, y = .6, width = .35, height = .35)
bites_min_plots_c

empty_plot <- ggplot() + theme_void()


behav_plots<-plot_grid(bites_min_plots_c, foray_plots_c, bites_foray_plots_c, empty_plot, tot_dist_plots_c,  mean_dist_plots_c,   ncol = 2, labels = "auto")
behav_plots


bite_plots<-plot_grid(bites_min_plots_c, foray_plots_c, bites_foray_plots_c,  ncol = 2, labels = "auto")
bite_plots


dist_plots<-plot_grid( tot_dist_plots_c,  mean_dist_plots_c,   ncol = 2, labels = "auto")
dist_plots


ggsave(filename = "../outputs/figures/n15_behavior_bite_plots_R1.jpg", 
       plot = bite_plots,
       width = 20,
      height = 20,
       units = "cm",
       dpi = 300)

ggsave(filename = "../outputs/figures/n15_behavior_distance_plots_R1.jpg", 
       plot = dist_plots,
       width = 20,
      height = 8,
       units = "cm",
       dpi = 300)



bite_plots2<-plot_grid(bites_min_plots_c, foray_plots_c, bites_foray_plots_c,  ncol = 3, labels = "auto")
bite_plots2

ggsave(filename = "../outputs/figures/n15_behavior_bite_plots_1row_R1.jpg", 
       plot = bite_plots2,
       width = 30,
      height = 10,
       units = "cm",
       dpi = 300)


```




####PLOT MODELS FOR OTHER PREDICTORS:------
#colors for bites =   scale_fill_manual(values = c( "lightgrey", "#40498EFF"))+ ##357BA2F
#colors for distance =  scale_fill_manual(values = c( "lightgrey", "#d0e2af"))+


###------------------------repeat total effect plots with centered and scaled: -------------


###run analysis - total and direct effect of n15 on total bites per minute------------
```{r, message=FALSE}
#start with no trial data----------
behav_dat_w_site_cs<-
  behav_dat_w_site%>%
  mutate(log_wave = log(wave_energy_manual))%>%
  mutate(N15_cs = base::scale(N15, center = TRUE, scale = TRUE),
          mean_atri_biomass_cs = base::scale(mean_atri_biomass, center = TRUE, scale = TRUE),
           mean_predator_biomass_cs = base::scale(mean_predator_biomass, center = TRUE, scale = TRUE),
          mean_damsel_biomass_cs = base::scale(mean_damsel_biomass, center = TRUE, scale = TRUE),
         mean_turf_obs_adjusted_cs = base::scale(mean_turf_obs_adjusted, center = TRUE, scale = TRUE),
         mean_structure_cs =  base::scale(mean_structure, center = TRUE, scale = TRUE),
         wave_cs = base::scale(wave_energy_manual, center = TRUE, scale = TRUE),
          log_wave_cs = base::scale(log_wave, center = TRUE, scale = TRUE),
         time_hours_cs = base::scale(time_hours, center = TRUE, scale = TRUE))%>%
  mutate(log_total_bites_per_minute = log(total_bites_per_minute))


###Run models TOTAL EFFECT--------
total_bites_n15_mod_site_loglink_option3s <-
  brm(total_bites_per_minute ~ N15_cs + log_wave_cs +  (1|site),
                data=behav_dat_w_site_cs, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_bites_n15_mod_site_loglink_option3s") #worked
print(total_bites_n15_mod_site_loglink_option3s)

```


###compare to other potential causes of behavior: 
```{r}

#####Aggressive encounters----------------
total_and_direct_bites_mod_site_loglink_aggressions <-
  brm(total_bites_per_minute ~ Binary_chases + mean_atri_biomass_cs + mean_damsel_biomass_cs  +  (1|site),
                data=behav_dat_w_site_cs, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_and_direct_bites_mod_site_loglink_aggressions") #worked
print(total_and_direct_bites_mod_site_loglink_aggressions)



#####A tri biomass----------------
total_bites_mod_site_loglink_atribios <-
  brm(total_bites_per_minute ~ mean_atri_biomass_cs +  N15_cs + mean_predator_biomass_cs + mean_structure_cs  + mean_turf_obs_adjusted_cs +  (1|site),
                data=behav_dat_w_site_cs, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_bites_mod_site_loglink_atribios") #2 divergent
print(total_bites_mod_site_loglink_atribios)


####Damselfish----------------
total_bites_mod_site_loglink_damsels <-
  brm(total_bites_per_minute ~ mean_damsel_biomass_cs + mean_predator_biomass_cs + mean_structure_cs  +  (1|site),
                data=behav_dat_w_site_cs, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_bites_mod_site_loglink_damsels") #worked
print(total_bites_mod_site_loglink_damsels)


####---------Predators---------
total_bites_mod_site_loglink_preds <-
  brm(total_bites_per_minute ~ mean_predator_biomass_cs + mean_structure_cs  +  (1|site),
                data=behav_dat_w_site_cs, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_bites_mod_site_loglink_preds") #worked
print(total_bites_mod_site_loglink_preds)



####---------Structure---------
total_bites_mod_site_loglink_structs <-
  brm(total_bites_per_minute ~ mean_structure_cs  + log_wave_cs +  (1|site),
                data=behav_dat_w_site_cs, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_bites_mod_site_loglink_structs") #worked
print(total_bites_mod_site_loglink_structs)



####---------Time of day---------
total_direct_bites_mod_site_loglink_times <-
  brm(total_bites_per_minute ~ time_hours_cs   +  (1|site),
                data=behav_dat_w_site_cs, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_direct_bites_mod_site_loglink_times") #worked
print(total_direct_bites_mod_site_loglink_times)



####---------Turf cover---------
total_bites_mod_site_loglink_turfs <-
  brm(total_bites_per_minute ~ mean_turf_obs_adjusted_cs   +  mean_damsel_biomass_cs  + N15_cs + mean_structure_cs + (1|site),
                data=behav_dat_w_site_cs, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_bites_mod_site_loglink_turfs") #worked
print(total_bites_mod_site_loglink_turfs)



####---------individual size---------
behav_dat_w_site_cs_size<-
  behav_dat_w_site_cs%>%
   mutate(TL_cm_cs = base::scale(Size, center = TRUE, scale = TRUE))


total_bites_mod_site_loglink_sizes <-
  brm(total_bites_per_minute ~ TL_cm_cs + (1|site),
                data=behav_dat_w_site_cs_size, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_bites_mod_site_loglink_sizes") #worked
print(total_bites_mod_site_loglink_sizes)


```


####repeat with all other behavior variables-----------
```{r}
#use: sum_distance_between_forays_per_minute  - this is the total distance travelled between forays, but scaled per minute so time doesn't matter.
#goes to 0....so add 1?

##add log column to dataframes:
behav_dat_w_site_cs_dist<-
  behav_dat_w_site_cs%>%
  mutate(sum_dist_foray_min_plus1 = sum_distance_between_forays_per_minute+1,
         mean_dist_foray_min_plus1 = mean_distance_between_forays+1,
         distance_end_start = as.numeric(Distance_end_start_m_formatted),
        distance_end_start_plus1 = distance_end_start+1 )

```



###run analysis - total and direct effect of n15 on total sumdist per minute - NEW DAGS - log------------
```{r, message=FALSE}

###Run models TOTAL EFFECT--------
total_sumdist_n15_mod_site_loglink_option3s <-
  brm(sum_dist_foray_min_plus1 ~ N15_cs + log_wave_cs +  (1|site),
                data=behav_dat_w_site_cs_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_sumdist_n15_mod_site_loglink_option3s") #worked
print(total_sumdist_n15_mod_site_loglink_option3s)

```


###compare to other potential causes of behavior: 
```{r, message=FALSE}

#####Aggressive encounters----------------
total_and_direct_sumdist_mod_site_loglink_aggressions <-
  brm(sum_dist_foray_min_plus1 ~ Binary_chases + mean_atri_biomass_cs + mean_damsel_biomass_cs  +  (1|site),
                data=behav_dat_w_site_cs_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_and_direct_sumdist_mod_site_loglink_aggressions") #worked
print(total_and_direct_sumdist_mod_site_loglink_aggressions)


#####A tri biomass----------------
total_sumdist_mod_site_loglink_atribios <-
  brm(sum_dist_foray_min_plus1 ~ mean_atri_biomass_cs +  N15_cs + mean_predator_biomass_cs + mean_structure_cs  + mean_turf_obs_adjusted_cs +  (1|site),
                data=behav_dat_w_site_cs_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_sumdist_mod_site_loglink_atribios") #2 divergent
print(total_sumdist_mod_site_loglink_atribios)


####Damselfish----------------
total_sumdist_mod_site_loglink_damsels <-
  brm(sum_dist_foray_min_plus1 ~ mean_damsel_biomass_cs + mean_predator_biomass_cs + mean_structure_cs  +  (1|site),
                data=behav_dat_w_site_cs_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_sumdist_mod_site_loglink_damsels") #worked
print(total_sumdist_mod_site_loglink_damsels)

####---------Predators---------
total_sumdist_mod_site_loglink_preds <-
  brm(sum_dist_foray_min_plus1 ~ mean_predator_biomass_cs + mean_structure_cs  +  (1|site),
                data=behav_dat_w_site_cs_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_sumdist_mod_site_loglink_preds") #worked
print(total_sumdist_mod_site_loglink_preds)



####---------Structure---------
total_sumdist_mod_site_loglink_structs <-
  brm(sum_dist_foray_min_plus1 ~ mean_structure_cs  + log_wave_cs +  (1|site),
                data=behav_dat_w_site_cs_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_sumdist_mod_site_loglink_structs") #worked
print(total_sumdist_mod_site_loglink_structs)




####---------Time of day---------
total_direct_sumdist_mod_site_loglink_times <-
  brm(sum_dist_foray_min_plus1 ~ time_hours_cs   +  (1|site),
                data=behav_dat_w_site_cs_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_direct_sumdist_mod_site_loglink_times") #worked
print(total_direct_sumdist_mod_site_loglink_times)


####---------Turf cover---------
total_sumdist_mod_site_loglink_turfs <-
  brm(sum_dist_foray_min_plus1 ~ mean_turf_obs_adjusted_cs   +  mean_damsel_biomass_cs  + N15_cs + mean_structure_cs + (1|site),
                data=behav_dat_w_site_cs_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_sumdist_mod_site_loglink_turfs") #worked
print(total_sumdist_mod_site_loglink_turfs)



####individual size--------------------------
behav_dat_w_site_cs_dist_size<-
  behav_dat_w_site_cs_dist%>%
   mutate(TL_cm_cs = base::scale(Size, center = TRUE, scale = TRUE))


total_sumdist_mod_site_loglink_sizes <-
  brm(sum_dist_foray_min_plus1 ~ TL_cm_cs + (1|site),
                data=behav_dat_w_site_cs_dist_size, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_sumdist_mod_site_loglink_sizes") #worked
print(total_sumdist_mod_site_loglink_sizes)


```



###MEAN DISTANCE PER FORAY CS-------------
```{r, message=FALSE}

###Run models TOTAL EFFECT--------
total_meandist_n15_mod_site_loglink_option3s <-
  brm(mean_dist_foray_min_plus1 ~ N15_cs + log_wave_cs +  (1|site),
                data=behav_dat_w_site_cs_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_meandist_n15_mod_site_loglink_option3s") #worked
print(total_meandist_n15_mod_site_loglink_option3s)


```




###compare to other potential causes of behavior: Mean dist CS
```{r, message=FALSE}

#####Aggressive encounters----------------
total_and_direct_meandist_mod_site_loglink_aggressions <-
  brm(mean_dist_foray_min_plus1 ~ Binary_chases + mean_atri_biomass_cs + mean_damsel_biomass_cs  +  (1|site),
                data=behav_dat_w_site_cs_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_and_direct_meandist_mod_site_loglink_aggressions") #worked
print(total_and_direct_meandist_mod_site_loglink_aggressions)


#####A tri biomass----------------
total_meandist_mod_site_loglink_atribios <-
  brm(mean_dist_foray_min_plus1 ~ mean_atri_biomass_cs +  N15_cs + mean_predator_biomass_cs + mean_structure_cs  + mean_turf_obs_adjusted_cs +  (1|site),
                data=behav_dat_w_site_cs_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_meandist_mod_site_loglink_atribios") #2 divergent
print(total_meandist_mod_site_loglink_atribios)



####Damselfish----------------
total_meandist_mod_site_loglink_damsels <-
  brm(mean_dist_foray_min_plus1 ~ mean_damsel_biomass_cs + mean_predator_biomass_cs + mean_structure_cs  +  (1|site),
                data=behav_dat_w_site_cs_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_meandist_mod_site_loglink_damsels") #worked
print(total_meandist_mod_site_loglink_damsels)



####---------Predators---------
total_meandist_mod_site_loglink_preds <-
  brm(mean_dist_foray_min_plus1 ~ mean_predator_biomass_cs + mean_structure_cs  +  (1|site),
                data=behav_dat_w_site_cs_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_meandist_mod_site_loglink_preds") #worked
print(total_meandist_mod_site_loglink_preds)


####---------Structure---------
total_meandist_mod_site_loglink_structs <-
  brm(mean_dist_foray_min_plus1 ~ mean_structure_cs  + log_wave_cs +  (1|site),
                data=behav_dat_w_site_cs_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_meandist_mod_site_loglink_structs") #worked
print(total_meandist_mod_site_loglink_structs)




####---------Time of day---------
total_direct_meandist_mod_site_loglink_times <-
  brm(mean_dist_foray_min_plus1 ~ time_hours_cs   +  (1|site),
                data=behav_dat_w_site_cs_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_direct_meandist_mod_site_loglink_times") #worked
print(total_direct_meandist_mod_site_loglink_times)



####---------Turf cover---------
total_meandist_mod_site_loglink_turfs <-
  brm(mean_dist_foray_min_plus1 ~ mean_turf_obs_adjusted_cs   +  mean_damsel_biomass_cs  + N15_cs + mean_structure_cs + (1|site),
                data=behav_dat_w_site_cs_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_meandist_mod_site_loglink_turfs") #worked
print(total_meandist_mod_site_loglink_turfs)


####----individual size
total_meandist_mod_site_loglink_sizes <-
  brm(mean_dist_foray_min_plus1 ~ TL_cm_cs + (1|site),
                data=behav_dat_w_site_cs_dist_size, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_meandist_mod_site_loglink_sizes") #worked
print(total_meandist_mod_site_loglink_sizes)

```



###------number of feeding bouts------

##n15 effects on feeding bouts per minute
```{r, message=FALSE}

#NEED TO SCALE BY MINUTE*****
behav_dat_w_site_cs_dist_foray<-
  behav_dat_w_site_cs_dist%>%
  mutate(forays_per_minute = number_forays/(total_time_seconds_numeric/60))

###Run models--------

###Run models TOTAL EFFECT--------
total_forays_n15_mod_site_loglink_option3s <-
  brm(forays_per_minute ~ N15_cs + log_wave_cs +  (1|site),
                data=behav_dat_w_site_cs_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_forays_n15_mod_site_loglink_option3s") #worked
print(total_forays_n15_mod_site_loglink_option3s)

```






###compare to other potential causes of behavior: # of forays
```{r, message=FALSE}

#####Aggressive encounters----------------
total_and_direct_forays_mod_site_loglink_aggressions <-
  brm(forays_per_minute ~ Binary_chases + mean_atri_biomass_cs + mean_damsel_biomass_cs  +  (1|site),
                data=behav_dat_w_site_cs_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_and_direct_forays_mod_site_loglink_aggressions") #worked
print(total_and_direct_forays_mod_site_loglink_aggressions)



#####A tri biomass----------------
total_forays_mod_site_loglink_atribios <-
  brm(forays_per_minute ~ mean_atri_biomass_cs +  N15_cs + mean_predator_biomass_cs + mean_structure_cs  + mean_turf_obs_adjusted_cs+  (1|site),
                data=behav_dat_w_site_cs_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_forays_mod_site_loglink_atribios") #2 divergent
print(total_forays_mod_site_loglink_atribios)


####Damselfish----------------
total_forays_mod_site_loglink_damsels <-
  brm(forays_per_minute ~ mean_damsel_biomass_cs + mean_predator_biomass_cs + mean_structure_cs  +  (1|site),
                data=behav_dat_w_site_cs_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_forays_mod_site_loglink_damsels") #worked
print(total_forays_mod_site_loglink_damsels)



####---------Predators---------
total_forays_mod_site_loglink_preds <-
  brm(forays_per_minute ~ mean_predator_biomass_cs + mean_structure_cs  +  (1|site),
                data=behav_dat_w_site_cs_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_forays_mod_site_loglink_preds") #worked
print(total_forays_mod_site_loglink_preds)



####---------Structure---------
total_forays_mod_site_loglink_structs <-
  brm(forays_per_minute ~ mean_structure_cs  + log_wave_cs +  (1|site),
                data=behav_dat_w_site_cs_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_forays_mod_site_loglink_structs") #worked
print(total_forays_mod_site_loglink_structs)



####---------Time of day---------
total_direct_forays_mod_site_loglink_times <-
  brm(forays_per_minute ~ time_hours_cs   +  (1|site),
                data=behav_dat_w_site_cs_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_direct_forays_mod_site_loglink_times") #worked
print(total_direct_forays_mod_site_loglink_times)



####---------Turf cover---------
total_forays_mod_site_loglink_turfs <-
  brm(forays_per_minute ~ mean_turf_obs_adjusted_cs   +  mean_damsel_biomass_cs  + N15_cs + mean_structure_cs + (1|site),
                data=behav_dat_w_site_cs_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_forays_mod_site_loglink_turfs") #worked
print(total_forays_mod_site_loglink_turfs)


####---------individual size---------

behav_dat_w_site_cs_dist_foray_size<-
  behav_dat_w_site_cs_dist_foray%>%
  ungroup()%>%
  mutate(TL_cm_cs = base::scale(Size, center = TRUE, scale = TRUE))


total_forays_mod_site_loglink_sizes <-
  brm(forays_per_minute ~ TL_cm_cs + (1|site),
                data=behav_dat_w_site_cs_dist_foray_size, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_forays_mod_site_loglink_sizes") #worked
print(total_forays_mod_site_loglink_sizes)


```






###bites per bout: mean_bites_per_foray --------


##n15 effects on mean_bites_per_foray
```{r, message=FALSE}

###Run models--------

###Run models TOTAL EFFECT--------
total_foraybites_n15_mod_site_loglink_option3s <-
  brm(mean_bites_per_foray ~ N15_cs + log_wave_cs +  (1|site),
                data=behav_dat_w_site_cs_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_foraybites_n15_mod_site_loglink_option3s") #worked
print(total_foraybites_n15_mod_site_loglink_option3s)


```



###compare to other cuases of behavior - BITES PER FORAY
```{r, message=FALSE}

#####Aggressive encounters----------------
total_and_direct_foraybites_mod_site_loglink_aggressions <-
  brm(mean_bites_per_foray ~ Binary_chases + mean_atri_biomass_cs + mean_damsel_biomass_cs  +  (1|site),
                data=behav_dat_w_site_cs_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_and_direct_foraybites_mod_site_loglink_aggressions") #worked
print(total_and_direct_foraybites_mod_site_loglink_aggressions)




#####A tri biomass----------------
total_foraybites_mod_site_loglink_atribios <-
  brm(mean_bites_per_foray ~ mean_atri_biomass_cs +  N15_cs + mean_predator_biomass_cs + mean_structure_cs  + mean_turf_obs_adjusted_cs +  (1|site),
                data=behav_dat_w_site_cs_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_foraybites_mod_site_loglink_atribios") #2 divergent
print(total_foraybites_mod_site_loglink_atribios)



####Damselfish----------------
total_foraybites_mod_site_loglink_damsels <-
  brm(mean_bites_per_foray ~ mean_damsel_biomass_cs + mean_predator_biomass_cs + mean_structure_cs  +  (1|site),
                data=behav_dat_w_site_cs_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_foraybites_mod_site_loglink_damsels") #worked
print(total_foraybites_mod_site_loglink_damsels)


####---------Predators---------
total_foraybites_mod_site_loglink_preds <-
  brm(mean_bites_per_foray ~ mean_predator_biomass_cs + mean_structure_cs  +  (1|site),
                data=behav_dat_w_site_cs_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_foraybites_mod_site_loglink_preds") #worked
print(total_foraybites_mod_site_loglink_preds)


####---------Structure---------
total_foraybites_mod_site_loglink_structs <-
  brm(mean_bites_per_foray ~ mean_structure_cs  + log_wave_cs +  (1|site),
                data=behav_dat_w_site_cs_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_foraybites_mod_site_loglink_structs") #worked
print(total_foraybites_mod_site_loglink_structs)


####---------Time of day---------
total_direct_foraybites_mod_site_loglink_times <-
  brm(mean_bites_per_foray ~ time_hours_cs   +  (1|site),
                data=behav_dat_w_site_cs_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_direct_foraybites_mod_site_loglink_times") #worked
print(total_direct_foraybites_mod_site_loglink_times)



####---------Turf cover---------
total_foraybites_mod_site_loglink_turfs <-
  brm(mean_bites_per_foray ~ mean_turf_obs_adjusted_cs   +  mean_damsel_biomass_cs  + N15_cs + mean_structure_cs + (1|site),
                data=behav_dat_w_site_cs_dist_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_foraybites_mod_site_loglink_turfs") #worked
print(total_foraybites_mod_site_loglink_turf)




total_foraybites_mod_site_loglink_sizes <-
  brm(mean_bites_per_foray ~ TL_cm_cs + (1|site),
                data=behav_dat_w_site_cs_dist_foray_size, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_foraybites_mod_site_loglink_sizes") #worked
print(total_foraybites_mod_site_loglink_sizes)


```




###PLOT CENTERED AND SCALED TOTAL EFFECTS--------
###bites plot:
```{r}

###combine all together: ------

all_causal_plot_bites_cs<-
ggplot() +
      geom_vline(xintercept=0, lty=2, alpha = .5)+
  #forays: 
  stat_pointinterval(data = as_draws_df(total_forays_n15_mod_site_loglink_option3s ), aes(x = (b_N15_cs),  y = 1,  color = "2Mid"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
  stat_pointinterval(data = as_draws_df(total_forays_mod_site_loglink_turfs), aes(x = (b_mean_turf_obs_adjusted_cs),  y = 2,  color = "2Mid"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
  stat_pointinterval(data = as_draws_df(total_forays_mod_site_loglink_structs), aes(x = (b_mean_structure_cs),  y = 6,  color = "2Mid"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
      stat_pointinterval(data = as_draws_df(total_forays_mod_site_loglink_atribios), aes(x = (b_mean_atri_biomass_cs),  y = 5,  color = "2Mid"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
    stat_pointinterval(data = as_draws_df(total_forays_mod_site_loglink_preds), aes(x = (b_mean_predator_biomass_cs),  y = 7,  color = "2Mid"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
    stat_pointinterval(data = as_draws_df(total_forays_mod_site_loglink_damsels), aes(x = (b_mean_damsel_biomass_cs),  y = 8,  color = "2Mid"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
    stat_pointinterval(data = as_draws_df(total_direct_forays_mod_site_loglink_times), aes(x = (b_time_hours_cs),  y = 3,  color = "2Mid"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
      stat_pointinterval(data = as_draws_df(total_and_direct_forays_mod_site_loglink_aggressions), aes(x = (b_Binary_chasesYes),  y = 9,  color = "2Mid"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
         stat_pointinterval(data = as_draws_df(total_forays_mod_site_loglink_sizes), aes(x = (b_TL_cm_cs),  y = 4,  color = "2Mid"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
  
  #bites:
   stat_pointinterval(data = as_draws_df(total_bites_n15_mod_site_loglink_option3s ), aes(x = (b_N15_cs),  y = 1.1,   color = "1Dark"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
  stat_pointinterval(data = as_draws_df(total_bites_mod_site_loglink_turfs), aes(x = (b_mean_turf_obs_adjusted_cs),  y = 2.1,   color = "1Dark"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
  stat_pointinterval(data = as_draws_df(total_bites_mod_site_loglink_structs), aes(x = (b_mean_structure_cs),  y = 6.1,   color = "1Dark"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
      stat_pointinterval(data = as_draws_df(total_bites_mod_site_loglink_atribios), aes(x = (b_mean_atri_biomass_cs),  y = 5.1,   color = "1Dark"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
    stat_pointinterval(data = as_draws_df(total_bites_mod_site_loglink_preds), aes(x = (b_mean_predator_biomass_cs),  y = 7.1,   color = "1Dark"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
    stat_pointinterval(data = as_draws_df(total_bites_mod_site_loglink_damsels), aes(x = (b_mean_damsel_biomass_cs),  y = 8.1,   color = "1Dark"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
    stat_pointinterval(data = as_draws_df(total_direct_bites_mod_site_loglink_times), aes(x = (b_time_hours_cs),  y = 3.1,   color = "1Dark"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
      stat_pointinterval(data = as_draws_df(total_and_direct_bites_mod_site_loglink_aggressions), aes(x = (b_Binary_chasesYes),  y = 9.1,   color = "1Dark"), 
               point_interval=median_hdi, .width=c(.9,.8)) +
         stat_pointinterval(data = as_draws_df(total_bites_mod_site_loglink_sizes), aes(x = (b_TL_cm_cs),  y = 4.1,  color = "1Dark"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
  
  #bites per foray: 
   stat_pointinterval(data = as_draws_df(total_foraybites_n15_mod_site_loglink_option3s ), aes(x = (b_N15_cs),  y = .9,  color = "3Light"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
  stat_pointinterval(data = as_draws_df(total_foraybites_mod_site_loglink_turfs), aes(x = (b_mean_turf_obs_adjusted_cs),  y = 1.9,  color = "3Light"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
  stat_pointinterval(data = as_draws_df(total_foraybites_mod_site_loglink_structs), aes(x = (b_mean_structure_cs),  y = 5.9,  color = "3Light"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
      stat_pointinterval(data = as_draws_df(total_foraybites_mod_site_loglink_atribios), aes(x = (b_mean_atri_biomass_cs),  y = 4.9,  color = "3Light"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
    stat_pointinterval(data = as_draws_df(total_foraybites_mod_site_loglink_preds), aes(x = (b_mean_predator_biomass_cs),  y = 6.9,  color = "3Light"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
    stat_pointinterval(data = as_draws_df(total_foraybites_mod_site_loglink_damsels), aes(x = (b_mean_damsel_biomass_cs),  y = 7.9,  color = "3Light"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
    stat_pointinterval(data = as_draws_df(total_direct_foraybites_mod_site_loglink_times), aes(x = (b_time_hours_cs),  y = 2.9,  color = "3Light"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
      stat_pointinterval(data = as_draws_df(total_and_direct_foraybites_mod_site_loglink_aggressions), aes(x = (b_Binary_chasesYes),  y = 8.9,  color = "3Light"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
        stat_pointinterval(data = as_draws_df(total_foraybites_mod_site_loglink_sizes), aes(x = (b_TL_cm_cs),  y = 3.9,  color = "3Light"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
  
  scale_y_continuous(breaks = c(9, 8, 7, 6,  5, 4, 3, 2, 1), labels = c("Aggressive encounters", "Damselfish biomass",  "Predator biomass", "Structural complexity","Surgeonfish biomass", "Surgeonfish size", "Time of day",  "Turf cover", expression(Turf~italic(delta)^15*N)))+ #"Turf nutrients" 
  
    scale_color_manual(values = c("1Dark" = "#20244D", "2Mid" = "#40498E", "3Light" = "#8CA0D9"),  name = " ", labels = c("Bites per minute", "Forays per minute", "Bites per foray"))+ 

   ylab("")+
   xlab("Effect on feeding rate metrics")+
  theme_bw()+
   theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(), 
        legend.position.inside = TRUE,
        legend.position = c(.99, .01),  
        legend.justification = c("right", "bottom"),
        rect = element_rect(fill = "transparent"),  
        plot.background = element_rect(fill = "transparent", color = NA),
        text=element_text(size=17)) #,  family="sans"

all_causal_plot_bites_cs

```



###distance plots
```{r}
###combined:
all_causal_plot_dist2_cs<-
ggplot() +
      geom_vline(xintercept=0, lty=2, alpha = .5)+

  #forays: 
  stat_pointinterval(data = as_draws_df(total_meandist_n15_mod_site_loglink_option3s ), aes(x = (b_N15_cs),  y = 1,  color = "2Light"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
  stat_pointinterval(data = as_draws_df(total_meandist_mod_site_loglink_turfs), aes(x = (b_mean_turf_obs_adjusted_cs),  y = 2,  color = "2Light"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
  stat_pointinterval(data = as_draws_df(total_meandist_mod_site_loglink_structs), aes(x = (b_mean_structure_cs),  y = 6,  color = "2Light"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
      stat_pointinterval(data = as_draws_df(total_meandist_mod_site_loglink_atribios), aes(x = (b_mean_atri_biomass_cs),  y = 5,  color = "2Light"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
    stat_pointinterval(data = as_draws_df(total_meandist_mod_site_loglink_preds), aes(x = (b_mean_predator_biomass_cs),  y = 7,  color = "2Light"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
    stat_pointinterval(data = as_draws_df(total_meandist_mod_site_loglink_damsels), aes(x = (b_mean_damsel_biomass_cs),  y =8,  color = "2Light"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
    stat_pointinterval(data = as_draws_df(total_direct_meandist_mod_site_loglink_times), aes(x = (b_time_hours_cs),  y = 3,  color = "2Light"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
      stat_pointinterval(data = as_draws_df(total_and_direct_meandist_mod_site_loglink_aggressions), aes(x = (b_Binary_chasesYes),  y = 9,  color = "2Light"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
           stat_pointinterval(data = as_draws_df(total_meandist_mod_site_loglink_sizes), aes(x = (b_TL_cm_cs),  y = 4,  color = "2Light"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
  #bites:
   stat_pointinterval(data = as_draws_df(total_sumdist_n15_mod_site_loglink_option3s ), aes(x = (b_N15_cs),  y = 1.1,   color = "1Dark"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
  stat_pointinterval(data = as_draws_df(total_sumdist_mod_site_loglink_turfs), aes(x = (b_mean_turf_obs_adjusted_cs),  y = 2.1,   color = "1Dark"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
  stat_pointinterval(data = as_draws_df(total_sumdist_mod_site_loglink_structs), aes(x = (b_mean_structure_cs),  y = 6.1,   color = "1Dark"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
      stat_pointinterval(data = as_draws_df(total_sumdist_mod_site_loglink_atribios), aes(x = (b_mean_atri_biomass_cs),  y = 5.1,   color = "1Dark"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
    stat_pointinterval(data = as_draws_df(total_sumdist_mod_site_loglink_preds), aes(x = (b_mean_predator_biomass_cs),  y = 7.1,   color = "1Dark"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
    stat_pointinterval(data = as_draws_df(total_sumdist_mod_site_loglink_damsels), aes(x = (b_mean_damsel_biomass_cs),  y = 8.1,   color = "1Dark"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
    stat_pointinterval(data = as_draws_df(total_direct_sumdist_mod_site_loglink_times), aes(x = (b_time_hours_cs),  y = 3.1,   color = "1Dark"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
      stat_pointinterval(data = as_draws_df(total_and_direct_sumdist_mod_site_loglink_aggressions), aes(x = (b_Binary_chasesYes),  y = 9.1,   color = "1Dark"), 
               point_interval=median_hdi, .width=c(.9,.8)) +
             stat_pointinterval(data = as_draws_df(total_sumdist_mod_site_loglink_sizes), aes(x = (b_TL_cm_cs),  y = 4.1,  color = "1Dark"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
  
  scale_y_continuous(breaks = c(9, 8, 7, 6,  5, 4, 3, 2, 1), labels = c("", "",  "", "","",  "",  "",  "" ,  ""  ))+
  
    scale_color_manual(values = c("1Dark" =  "#5a7d4e", "2Light" = "#d0e2af"),  name = " ", labels = c("Distance per minute", "Distance per foray"))+ 

   ylab("")+
   xlab("Effect on distance metrics")+
  theme_bw()+
   theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(), 
        legend.position.inside = TRUE,
        legend.position = c(.01, .01),  
        legend.justification = c("left", "bottom"),
        rect = element_rect(fill = "transparent"),  
        plot.background = element_rect(fill = "transparent", color = NA),
        text=element_text(size=17)) #,  family="sans"

all_causal_plot_dist2_cs

```


##plot all:
```{r}

##only one label set
behav_dist_comb_plots2_cs<-plot_grid(all_causal_plot_bites_cs, all_causal_plot_dist2_cs, ncol = 2, labels = "auto", rel_widths = c(1, .72), label_x = c(.3, 0))
behav_dist_comb_plots2_cs



ggsave(filename = "../outputs/figures/behavior_and_distance_all_causal_plots_scaled_R1.jpg", 
       plot = behav_dist_comb_plots2_cs,
   width = 30,
      height = 25,
       units = "cm",
       dpi = 300)



```
