---
title: "checking_alt_adj_sets"
output: html_document
date: "2026-07-15"
---


###when reverse directionality, only one adjustment sets that change are: 

#would need to add in demographic effect on behaviour: 

#(1) adjustmentSets(full_dag_1, exposure = "atri_dem", outcome = "atri_behavior", type = "minimal", effect = c("total"))
#{ atri_biomass, n15, predators, size, structure, turf_cover }

#(2) adjustmentSets(full_dag_2, exposure = "atri_biomass", outcome = "atri_behavior", type = "minimal", effect = c("total"))
#{ atri_dem, n15, predators, structure, turf_cover }

#and that's it!

##load packages
```{r, warning = FALSE, message = FALSE, results = FALSE, fig.show='hide'}
library(tidyverse) #for everything

library(cowplot) #for combining plots

#for bayesian modelling and interpreting:
library(brms)
library(tidybayes)
library(emmeans)
library(tidybayes)
library(modelr)

```


#load data: 
```{r, warning = FALSE, message = FALSE, results = FALSE}
behav_dat_w_site<-read.csv("../data/behav_w_site_dat.csv")
behav_dat_w_site


behav_dat_w_site_c2<-
  behav_dat_w_site%>%
  mutate(N15_c = base::scale(N15, center = TRUE, scale = FALSE),
          mean_atri_biomass_c = base::scale(mean_atri_biomass, center = TRUE, scale = FALSE),
           mean_predator_biomass_c = base::scale(mean_predator_biomass, center = TRUE, scale = FALSE),
         mean_turf_obs_adjusted_c = base::scale(mean_turf_obs_adjusted, center = TRUE, scale = FALSE),
         mean_structure_c =  base::scale(mean_structure, center = TRUE, scale = FALSE),
         mean_seabird_n_input_c =  base::scale(mean_seabird_n_input, center = TRUE, scale = FALSE),
        size_c =  base::scale(Size, center = TRUE, scale = FALSE),
      mean_hsi_c =  base::scale(hsi, center = TRUE, scale = FALSE),
        mean_growth_c =  base::scale(growth_resid, center = TRUE, scale = FALSE) )%>%
  mutate(log_total_bites_per_minute = log(total_bites_per_minute))


```


#(1) adjustmentSets(full_dag_1, exposure = "atri_dem", outcome = "atri_behavior", type = "minimal", effect = c("total"))
#{ atri_biomass, n15, predators, size, structure, turf_cover }
```{r}
###Run models TOTAL BITES--------
total_bites_growth_mod_site_loglink_alt <-
  brm(total_bites_per_minute ~mean_growth_c+ N15_c + mean_turf_obs_adjusted_c + mean_atri_biomass_c + mean_predator_biomass_c + mean_structure_c + size_c + (1|site),
                data=behav_dat_w_site_c2, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_bites_growth_mod_site_loglink_alt") #worked
print(total_bites_growth_mod_site_loglink_alt)

plot(total_bites_growth_mod_site_loglink_alt, ask = FALSE)
pp_check(total_bites_growth_mod_site_loglink_alt)
#looks good

hypothesis(total_bites_growth_mod_site_loglink_alt, "mean_growth_c<0") #0.45 - so no effect

total_bites_growth_mod_site_loglink_alt%>%
  spread_draws(b_mean_growth_c)%>%
  median_hdi(exp(b_mean_growth_c))

###Run models TOTAL BITES--------
total_bites_hsi_mod_site_loglink_alt <-
  brm(total_bites_per_minute ~mean_hsi_c+ N15_c + mean_turf_obs_adjusted_c + mean_atri_biomass_c + mean_predator_biomass_c + mean_structure_c + size_c + (1|site),
                data=behav_dat_w_site_c2, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_bites_hsi_mod_site_loglink_alt") #worked
print(total_bites_hsi_mod_site_loglink_alt)
#DIDNT WORK***


#run model - sumdist ----
behav_dat_w_site_c2_dist<-
  behav_dat_w_site_c2%>%
  mutate(sum_dist_foray_min_plus1 = sum_distance_between_forays_per_minute+1,
         mean_dist_foray_min_plus1 = mean_distance_between_forays+1,
         distance_end_start = as.numeric(Distance_end_start_m_formatted),
        distance_end_start_plus1 = distance_end_start+1 )


sum_dist_growth_mod_site_loglink_alt <-
  brm(sum_dist_foray_min_plus1 ~mean_growth_c+ N15_c + mean_turf_obs_adjusted_c + mean_atri_biomass_c + mean_predator_biomass_c + mean_structure_c + size_c + (1|site),
                data=behav_dat_w_site_c2_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/sum_dist_growth_mod_site_loglink_alt") #worked
print(sum_dist_growth_mod_site_loglink_alt)

plot(sum_dist_growth_mod_site_loglink_alt, ask = FALSE)
pp_check(sum_dist_growth_mod_site_loglink_alt)
#looks good

hypothesis(sum_dist_growth_mod_site_loglink_alt, "mean_growth_c<0") #0.71 - so not much effect...large uncertainty intervals


#run model: mean_dist_foray_min_plus1----
mean_dist_growth_mod_site_loglink_alt <-
  brm(mean_dist_foray_min_plus1 ~mean_growth_c+ N15_c + mean_turf_obs_adjusted_c + mean_atri_biomass_c + mean_predator_biomass_c + mean_structure_c + size_c + (1|site),
                data=behav_dat_w_site_c2_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/mean_dist_growth_mod_site_loglink_alt") #worked
print(mean_dist_growth_mod_site_loglink_alt)

plot(mean_dist_growth_mod_site_loglink_alt, ask = FALSE)
pp_check(mean_dist_growth_mod_site_loglink_alt)
#looks good

hypothesis(mean_dist_growth_mod_site_loglink_alt, "mean_growth_c<0") #0.69 - so no effect


#forays----
behav_dat_w_site_c2_foray<-
  behav_dat_w_site_c2%>%
  mutate(forays_per_minute = number_forays/(total_time_seconds_numeric/60))


foray_growth_mod_site_loglink_alt <-
  brm(forays_per_minute ~mean_growth_c+ N15_c + mean_turf_obs_adjusted_c + mean_atri_biomass_c + mean_predator_biomass_c + mean_structure_c + size_c + (1|site),
                data=behav_dat_w_site_c2_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/foray_growth_mod_site_loglink_alt") #worked
print(foray_growth_mod_site_loglink_alt)

plot(foray_growth_mod_site_loglink_alt, ask = FALSE)
pp_check(foray_growth_mod_site_loglink_alt)
#looks good

hypothesis(foray_growth_mod_site_loglink_alt, "mean_growth_c<0") #0.5 - so no effect


```


#(2) adjustmentSets(full_dag_2, exposure = "atri_biomass", outcome = "atri_behavior", type = "minimal", effect = c("total"))
#{ atri_dem, n15, predators, structure, turf_cover }
```{r}
###Run models TOTAL BITES--------
total_bites_biomass_mod_site_loglink_alt <-
  brm(total_bites_per_minute ~mean_growth_c+ N15_c + mean_turf_obs_adjusted_c + mean_atri_biomass_c + mean_predator_biomass_c + mean_structure_c + (1|site),
                data=behav_dat_w_site_c2, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/total_bites_biomass_mod_site_loglink_alt") #worked
print(total_bites_biomass_mod_site_loglink_alt)

plot(total_bites_biomass_mod_site_loglink_alt, ask = FALSE)
pp_check(total_bites_biomass_mod_site_loglink_alt)
#looks good

hypothesis(total_bites_biomass_mod_site_loglink_alt, "mean_atri_biomass_c<0") #0.41 - so no effect

total_bites_biomass_mod_site_loglink_alt%>%
  spread_draws(b_mean_atri_biomass_c)%>%
  median_hdi(exp(b_mean_atri_biomass_c))

sum_dist_biomass_mod_site_loglink_alt <-
  brm(sum_dist_foray_min_plus1 ~mean_growth_c+ N15_c + mean_turf_obs_adjusted_c + mean_atri_biomass_c + mean_predator_biomass_c + mean_structure_c  + (1|site),
                data=behav_dat_w_site_c2_dist, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/sum_dist_biomass_mod_site_loglink_alt") #worked
print(sum_dist_biomass_mod_site_loglink_alt)

plot(sum_dist_biomass_mod_site_loglink_alt, ask = FALSE)
pp_check(sum_dist_biomass_mod_site_loglink_alt)
#looks good

hypothesis(sum_dist_biomass_mod_site_loglink_alt, "mean_atri_biomass_c<0") #0.68 - so not much effect...large uncertainty intervals
sum_dist_biomass_mod_site_loglink_alt%>%
  spread_draws(b_mean_atri_biomass_c)%>%
  median_hdi(exp(b_mean_atri_biomass_c))





foray_biomass_mod_site_loglink_alt <-
  brm(forays_per_minute ~mean_growth_c+ N15_c + mean_turf_obs_adjusted_c + mean_atri_biomass_c + mean_predator_biomass_c + mean_structure_c  + (1|site),
                data=behav_dat_w_site_c2_foray, family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/foray_biomass_mod_site_loglink_alt") #worked
print(foray_biomass_mod_site_loglink_alt)

plot(foray_biomass_mod_site_loglink_alt, ask = FALSE)
pp_check(foray_biomass_mod_site_loglink_alt)
#looks good

hypothesis(foray_growth_mod_site_loglink_alt, "mean_growth_c<0") #0.5 - so no effect
foray_biomass_mod_site_loglink_alt

```

