---
title: "DAG"
author: "CEB"
date: '2025-11-26'
output: html_document
---


#load packages
```{r}
library(tidyverse)
library(dagitty)
```



#Full dag from dagitty:
```{r}
full_dag<-
  dagitty("dag {
N_input -> turf_cover
N_input -> n15
aggression -> atri_behavior
atri_biomass -> aggression
atri_biomass -> atri_behavior
atri_biomass -> atri_dem
damselfish_biomass -> aggression
damselfish_biomass -> atri_behavior
damselfish_biomass -> turf_cover
atri_behavior -> atri_dem
exposure -> N_input
exposure -> turf_cover
exposure -> n15
exposure -> structure
turf_cover -> atri_biomass
turf_cover -> atri_behavior
turf_cover -> atri_dem
n15 -> atri_biomass
n15 -> atri_behavior
n15 -> atri_dem
predators -> atri_biomass
predators -> damselfish_biomass
predators -> atri_behavior
predators -> atri_dem
size -> atri_behavior
size -> atri_dem
structure -> atri_biomass
structure -> damselfish_biomass
structure -> atri_behavior
structure -> atri_dem
structure -> turf_cover
structure -> predators
time -> atri_behavior
}")

```



#check adjustment sets
```{r}

#check adjustment sets - n15-----
adjustmentSets(full_dag, exposure = "N_input", outcome = "n15",
               type = "minimal", effect = c("total"))
#{ exposure }


adjustmentSets(full_dag, exposure = "exposure", outcome = "n15",
               type = "minimal", effect = c("total"))
#{}



#check adjustment sets - behavior-----
adjustmentSets(full_dag, exposure = "n15", outcome = "atri_behavior",
               type = "minimal", effect = c("total"))
#{ damselfish_biomass, structure, turf_cover }
#{ N_input, exposure }


adjustmentSets(full_dag, exposure = "turf_cover", outcome = "atri_behavior",
               type = "minimal", effect = c("total"))
#{ damselfish_biomass, n15, structure }
#{ N_input, damselfish_biomass, exposure, structure }


adjustmentSets(full_dag, exposure = "size", outcome = "atri_behavior",
               type = "minimal", effect = c("total"))
#none needed


adjustmentSets(full_dag, exposure = "aggression", outcome = "atri_behavior",
               type = "minimal", effect = c("total"))
#{ atri_biomass, damselfish_biomass }

adjustmentSets(full_dag, exposure = "time", outcome = "atri_behavior",
               type = "minimal", effect = c("total"))
#none needed

adjustmentSets(full_dag, exposure = "predators", outcome = "atri_behavior",
               type = "minimal", effect = c("total"))
#{ structure }


adjustmentSets(full_dag, exposure = "structure", outcome = "atri_behavior",
               type = "minimal", effect = c("total"))
#{ exposure }



adjustmentSets(full_dag, exposure = "atri_biomass", outcome = "atri_behavior",
               type = "minimal", effect = c("total"))
#{ n15, predators, structure, turf_cover }



#check adjustment sets - demographics-----
adjustmentSets(full_dag, exposure = "n15", outcome = "atri_dem",
               type = "minimal", effect = c("total"))
#{ damselfish_biomass, structure, turf_cover }
#{ N_input, exposure }


adjustmentSets(full_dag, exposure = "turf_cover", outcome = "atri_dem",
               type = "minimal", effect = c("total"))
#{ damselfish_biomass, n15, structure }
#{ N_input, damselfish_biomass, exposure, structure }


adjustmentSets(full_dag, exposure = "size", outcome = "atri_dem",
               type = "minimal", effect = c("total"))
#none needed


adjustmentSets(full_dag, exposure = "predators", outcome = "atri_dem",
               type = "minimal", effect = c("total"))
#{ structure }


adjustmentSets(full_dag, exposure = "structure", outcome = "atri_dem",
               type = "minimal", effect = c("total"))
#{ exposure }



adjustmentSets(full_dag, exposure = "atri_biomass", outcome = "atri_dem",
               type = "minimal", effect = c("total"))
#{ n15, predators, structure, turf_cover }



```






#copied from dagitty.net:
dag {
bb="0,0,1,1"
"N input" [pos="0.099,0.103"]
"aggressive encounters" [pos="0.828,0.592"]
"atri_biomass/density" [pos="0.571,0.042"]
"damselfish density/biomass" [pos="0.534,0.608"]
atri_behavior [pos="0.855,0.396"]
atri_dem [outcome,pos="0.831,0.199"]
exposure [pos="0.131,0.273"]
food_availability [pos="0.282,0.262"]
food_quality [pos="0.288,0.136"]
predators [pos="0.341,0.615"]
size [exposure,pos="0.939,0.240"]
structure [pos="0.278,0.433"]
"N input" -> food_availability
"N input" -> food_quality
"aggressive encounters" -> atri_behavior
"atri_biomass/density" -> "aggressive encounters"
"atri_biomass/density" -> atri_behavior
"atri_biomass/density" -> atri_dem
"damselfish density/biomass" -> "aggressive encounters"
"damselfish density/biomass" -> atri_behavior
"damselfish density/biomass" -> food_availability
atri_behavior -> atri_dem
exposure -> "N input"
exposure -> food_availability
exposure -> food_quality
exposure -> structure
food_availability -> "atri_biomass/density"
food_availability -> atri_behavior
food_availability -> atri_dem
food_quality -> "atri_biomass/density"
food_quality -> atri_behavior
food_quality -> atri_dem
predators -> "atri_biomass/density"
predators -> "damselfish density/biomass"
predators -> atri_behavior
predators -> atri_dem
size -> atri_behavior
size -> atri_dem
structure -> "atri_biomass/density"
structure -> "damselfish density/biomass"
structure -> atri_behavior
structure -> atri_dem
structure -> food_availability
structure -> predators
}

