---
title: "demoraphic-analysis"
author: "CEB"
date: '2025-12-10'
output: html_document
---



##load packages
```{r, warning = FALSE, message = FALSE, results = FALSE, fig.show='hide'}
library(tidyverse) #for everything

library(cowplot) #for combining plots

#for bayesian modelling and interpreting:
library(brms)
library(tidybayes)
library(emmeans)
library(tidybayes)
library(modelr)

```

#load data:
```{r, warning = FALSE, message = FALSE, results = FALSE, fig.show='hide'}
dem_dat_w_site<-read.csv("../data/dem_w_site_dat.csv")
dem_dat_w_site


dem_dat_w_site%>%
  group_by(site)%>%
  summarize(n_hsi = length(HSI),
            n_growth = length(Growth_residuals))

```

#check if should log some predictors:
```{r}
dem_dat_w_site%>%
  ggplot(aes(x = site, y = mean_predator_biomass))+
  geom_point()
#looks okay
  

dem_dat_w_site%>%
  ggplot(aes(x = site, y = wave_energy_manual))+
  geom_point()
#very skewed

hist(dem_dat_w_site$mean_predator_biomass)
hist(dem_dat_w_site$wave_energy_manual)
hist(dem_dat_w_site$mean_damsel_biomass)

```



###run HSI model based on DAGs for effect of N15-----
#direct effects not working, but total effect does******
```{r, message = FALSE}

range(dem_dat_w_site$mean_predator_biomass)
range(dem_dat_w_site$wave_energy_manual)
range(dem_dat_w_site$mean_damsel_biomass)

#center----
dem_dat_w_site_c<-
  dem_dat_w_site%>%
  ungroup()%>%
      mutate(log_HSI = log(HSI),
             log_wave_energy_manual = log(wave_energy_manual),
             mean_seabird_n_input_c = base::scale(mean_seabird_n_input, center = TRUE, scale = FALSE),
       Muscle_N15_c = base::scale(Muscle_N15, center = TRUE, scale = FALSE),
          mean_atri_biomass_c = base::scale(mean_atri_biomass, center = TRUE, scale = FALSE),
           mean_predator_biomass_c = base::scale(mean_predator_biomass, center = TRUE, scale = FALSE),
          mean_damsel_biomass_c = base::scale(mean_damsel_biomass, center = TRUE, scale = FALSE),
         mean_turf_obs_adjusted_c = base::scale(mean_turf_obs_adjusted, center = TRUE, scale = FALSE),
         mean_structure_c =  base::scale(mean_structure, center = TRUE, scale = FALSE),
         wave_c = base::scale(wave_energy_manual, center = TRUE, scale = FALSE),
         log_wave_c = base::scale(log_wave_energy_manual, center = TRUE, scale = FALSE),
       bites_per_minute_c = base::scale(bites_per_minute, center = TRUE, scale = FALSE),
       distance_per_minute_c = base::scale(distance_per_minute, center = TRUE, scale = FALSE))
  

###total effect wtih lognormal family :
mod_hsi_n15 <- brm(HSI  ~ Muscle_N15_c + mean_damsel_biomass_c + mean_structure_c + mean_turf_obs_adjusted_c + (1|site),
                data=dem_dat_w_site_c,family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/mod_hsi_n15") #worked
print(mod_hsi_n15)

plot(mod_hsi_n15, ask = FALSE)
pp_check(mod_hsi_n15) #looks good


hypothesis(mod_hsi_n15, c("Muscle_N15_c>0"))  #0.91 - still good. 


mod_hsi_n15%>%
  spread_draws(b_Muscle_N15_c)%>%
  median_hdi(exp(b_Muscle_N15_c))
#1.045613	0.975953	1.115186	
#quite close to all previous models
1-0.975953 #0.024047

#option 2:
mod_hsi_n15_option2 <- brm(HSI  ~ Muscle_N15_c + mean_seabird_n_input_c + log_wave_c + (1|site),
                data=dem_dat_w_site_c,family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/mod_hsi_n15_option2") #worked
print(mod_hsi_n15_option2)

plot(mod_hsi_n15_option2, ask = FALSE)
pp_check(mod_hsi_n15_option2) #looks good


hypothesis(mod_hsi_n15_option2, c("Muscle_N15_c>0"))  #0.94 - still good. 


mod_hsi_n15_option2%>%
  spread_draws(b_Muscle_N15_c)%>%
  median_hdi(exp(b_Muscle_N15_c))
#1.055931	0.9842174	1.128383		
#quite close to previous model, if antthing slightly stronger effect here



```



#Total effects of all variables on HSI:-----
```{r, message = FALSE}

###Atri biomass-----
mod_hsi_by_atri_bio <- brm(HSI  ~ mean_atri_biomass_c + mean_predator_biomass_c + mean_structure_c + mean_turf_obs_adjusted_c + Muscle_N15_c + (1|site),
                data=dem_dat_w_site_c,family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/mod_hsi_by_atri_bio") #worked
print(mod_hsi_by_atri_bio)

plot(mod_hsi_by_atri_bio, ask = FALSE)
pp_check(mod_hsi_by_atri_bio) #looks good

hypothesis(mod_hsi_by_atri_bio, c("mean_atri_biomass_c<0"))  #0.22

mod_hsi_by_atri_bio%>%
  spread_draws(b_mean_atri_biomass_c)%>%
  median_hdi(exp(b_mean_atri_biomass_c))
#1.00492	0.9878331	1.02163	

###Predators-----
mod_hsi_by_pred <- brm(HSI  ~  mean_predator_biomass_c + mean_structure_c  + (1|site),
                data=dem_dat_w_site_c,family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/mod_hsi_by_pred") #worked
print(mod_hsi_by_pred)

plot(mod_hsi_by_pred, ask = FALSE)
pp_check(mod_hsi_by_pred) #looks good

hypothesis(mod_hsi_by_pred, c("mean_predator_biomass_c<0")) #now 0.28

mod_hsi_by_pred%>%
  spread_draws(b_mean_predator_biomass_c)%>%
  median_hdi(exp(b_mean_predator_biomass_c))
#1.004382	0.9750079	1.032562	


###Structure-----
mod_hsi_by_struct <- brm(HSI  ~    mean_structure_c  + log_wave_c + (1|site),
                data=dem_dat_w_site_c,family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/mod_hsi_by_struct") #worked
print(mod_hsi_by_struct)

plot(mod_hsi_by_struct, ask = FALSE)
pp_check(mod_hsi_by_struct) #looks good

hypothesis(mod_hsi_by_struct, c("mean_structure_c>0"))  #.09 - so strong NEGATIVE effect of structure on hsi.
#this is total effect - so could be because affects predators, competitors, damselfish, behavior, etc. 

mod_hsi_by_struct%>%
  spread_draws(b_mean_structure_c)%>%
  median_hdi(exp(b_mean_structure_c))
#0.6375698	0.2567127	1.219539	0.95
1-0.6375698 #0.3624302 reduction
1-0.2567127 #0.7432873

mod_hsi_by_struct%>%
  spread_draws(b_mean_structure_c)%>%
  median_hdi(exp(-b_mean_structure_c))

###turf cover-----
mod_hsi_by_turf_cover<- brm(HSI  ~    mean_turf_obs_adjusted_c  + mean_damsel_biomass_c + Muscle_N15_c + mean_structure_c + (1|site),
                data=dem_dat_w_site_c,family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/mod_hsi_by_turf_cover") #worked
print(mod_hsi_by_turf_cover)

plot(mod_hsi_by_turf_cover, ask = FALSE)
pp_check(mod_hsi_by_turf_cover) #looks good

hypothesis(mod_hsi_by_turf_cover, c("mean_turf_obs_adjusted_c>0"))  #.69 - weak

mod_hsi_by_turf_cover%>%
  spread_draws(b_mean_turf_obs_adjusted_c)%>%
  median_hdi(exp(b_mean_turf_obs_adjusted_c))
#1.006036	0.9652339	1.047076	


###individual size-----
dem_dat_w_site_c_size<-
  dem_dat_w_site_c%>%
  mutate(TL_cm_c = base::scale(TL_cm, center = TRUE, scale = FALSE))

mod_hsi_by_size<- brm(HSI  ~    TL_cm_c  + (1|site),
                data=dem_dat_w_site_c_size,family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/mod_hsi_by_size") #worked
print(mod_hsi_by_size)

plot(mod_hsi_by_size, ask = FALSE)
pp_check(mod_hsi_by_size) #looks good

hypothesis(mod_hsi_by_size, c("TL_cm_c>0"))  #0.67 - weak

mod_hsi_by_size%>%
  spread_draws(b_TL_cm_c)%>%
  median_hdi(exp(b_TL_cm_c))
#1.024159	0.9118168	1.148187

```


###growth residuals models: ------
```{r}

###TOTAL effect of N15:---------
mod_growth_by_n15_option1 <- brm(Growth_residuals  ~ Muscle_N15_c + mean_damsel_biomass_c + mean_structure_c + mean_turf_obs_adjusted_c + (1|site),
                data=dem_dat_w_site_c,
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/mod_growth_by_n15_option1") #worked
print(mod_growth_by_n15_option1)

plot(mod_growth_by_n15_option1, ask = FALSE)
pp_check(mod_growth_by_n15_option1) #looks good


hypothesis(mod_growth_by_n15_option1, c("Muscle_N15_c>0"))  #0.3


mod_growth_by_n15_option1%>%
  spread_draws(b_Muscle_N15_c)%>%
  median_hdi(b_Muscle_N15_c)
#0.9978768	0.9892364	1.006101	



###Atri biomass-----
mod_growth_by_atri_bio <- brm(Growth_residuals  ~ mean_atri_biomass_c + mean_predator_biomass_c + mean_structure_c + mean_turf_obs_adjusted_c + Muscle_N15_c +  (1|site),
                data=dem_dat_w_site_c,
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/mod_growth_by_atri_bio") #worked
print(mod_growth_by_atri_bio)

plot(mod_growth_by_atri_bio, ask = FALSE)
pp_check(mod_growth_by_atri_bio) #looks good

hypothesis(mod_growth_by_atri_bio, c("mean_atri_biomass_c<0"))  #0.16 (so trending positive but not super strong)

mod_growth_by_atri_bio%>%
  spread_draws(b_mean_atri_biomass_c)%>%
  median_hdi(b_mean_atri_biomass_c)

###Predators-----
mod_growth_by_pred <- brm(Growth_residuals  ~  mean_predator_biomass_c + mean_structure_c  + (1|site),
                data=dem_dat_w_site_c,
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/mod_growth_by_pred") #worked
print(mod_growth_by_pred)

plot(mod_growth_by_pred, ask = FALSE)
pp_check(mod_growth_by_pred) #looks good

hypothesis(mod_growth_by_pred, c("mean_predator_biomass_c<0")) #.53 - not much happening

mod_growth_by_pred%>%
  spread_draws(b_mean_predator_biomass_c)%>%
  median_hdi((b_mean_predator_biomass_c))


##size
mod_growth_by_size<- brm(Growth_residuals  ~    TL_cm_c  + (1|site),
                data=dem_dat_w_site_c_size,
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/mod_growth_by_size") #worked
print(mod_growth_by_size)

plot(mod_growth_by_size, ask = FALSE)
pp_check(mod_growth_by_size) #looks good

hypothesis(mod_growth_by_size, c("TL_cm_c>0"))  #1 - strong positive effect***

mod_growth_by_size%>%
  spread_draws(b_TL_cm_c)%>%
  median_hdi((b_TL_cm_c))


###Structure-----
mod_growth_by_struct <- brm(Growth_residuals  ~    mean_structure_c  + log_wave_c + (1|site),
                data=dem_dat_w_site_c,
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/mod_growth_by_struct") #worked
print(mod_growth_by_struct)

plot(mod_growth_by_struct, ask = FALSE)
pp_check(mod_growth_by_struct) #looks good

hypothesis(mod_growth_by_struct, c("mean_structure_c>0"))  #0.04 - so strong NEGATIVE effect of structure on growth (similar to HSI)
#this is total effect - so could be because affects predators, behavior, etc. 

mod_growth_by_struct%>%
  spread_draws(b_mean_structure_c)%>%
  median_hdi((b_mean_structure_c))



###turf cover-----
mod_growth_by_turf_cover<- brm(Growth_residuals  ~    mean_turf_obs_adjusted_c  + mean_damsel_biomass_c + Muscle_N15_c + mean_structure_c + (1|site),
                data=dem_dat_w_site_c,
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/mod_growth_by_turf_cover") #worked
print(mod_growth_by_turf_cover)

plot(mod_growth_by_turf_cover, ask = FALSE)
pp_check(mod_growth_by_turf_cover) #looks good

hypothesis(mod_growth_by_turf_cover, c("mean_turf_obs_adjusted_c>0"))  #.4 - weak

mod_growth_by_turf_cover%>%
  spread_draws(b_mean_turf_obs_adjusted_c)%>%
  median_hdi((b_mean_turf_obs_adjusted_c))





```


###plots for total effect model - HSI-------
```{r}
##DAGS
#PLOTS:
hsi_dag_me<-conditional_effects(mod_hsi_n15, effects = "Muscle_N15_c", plot = FALSE)[[1]]
mean(dem_dat_w_site_c$Muscle_N15) #9.258909

hsi_dag_me_unscale<-
  hsi_dag_me%>%
  mutate(Muscle_N15 = Muscle_N15_c +9.258909)

hsi_draws<-
dem_dat_w_site_c %>%
  data_grid(Muscle_N15_c = seq_range(Muscle_N15_c, n = 50),
            mean_damsel_biomass_c = 0,
            mean_turf_obs_adjusted_c = 0,
            mean_structure_c = 0) %>%
  add_epred_draws(mod_hsi_n15, ndraws = 500, re_formula = NA)

hsi_draws_rescale<-
  hsi_draws%>%
  mutate(Muscle_N15 = Muscle_N15_c +9.258909)


hsi_draw_plot<-
dem_dat_w_site_c%>%
  ggplot(aes(x = Muscle_N15, y = HSI))+
  geom_line(data = hsi_draws_rescale, aes(y = .epred, x = Muscle_N15, group = .draw), color = "grey", alpha = .2, lwd = .5) +
    #ylab(expression(Surgeonfish~italic(delta)^15*N)) +
    # xlab(expression(Seabird~breeding~biomass~(kg~ha^-1))) +
     geom_line(data = hsi_dag_me_unscale, aes(y = estimate__), alpha = .9, lwd = 1) +
  # geom_point(color = "#d0e2af", fill = "#d0e2af", size = 4, alpha = .8)+
     geom_point(color = "#f5db99", fill = "#f5db99", size = 3, alpha = .8)+
       xlab(expression(Surgeonfish~italic(delta)^15*N)) +
  ylab("Condition (HSI)")+
  theme_bw() +
   theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.title = element_blank(),
        legend.direction = "horizontal",
       #legend.position = "none"#,
        legend.position = "inside",
        legend.position.inside = c(.8, .8)
       )

hsi_draw_plot



###posterior plot:
hsi_plot_post_dist_back<-
ggplot() +
     geom_vline(xintercept=1, lty=2, alpha = .5)+
  stat_halfeye(data = as_draws_df(mod_hsi_n15), aes(x = exp(b_Muscle_N15_c),  y = 1, fill =  after_stat(x< 1)), 
               point_interval=median_hdi, .width=c(.9,.8),  slab_alpha = .9) + 
#scale_fill_manual(values = c("#0072B2", "#D55E00"	))+
   scale_fill_manual(values = c("#f5db99", "lightgrey"	))+
  theme_minimal()+
   ylab("")+
   xlab(expression(Multiplicative~effect~of~surgeonfish~italic(delta)^15*N~on~HSI)) +
   ylab("")+
 # xlim(c(-1,2))+
   xlab("")+
  theme_bw()+
   theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(), 
        axis.ticks.y =  element_blank(), 
        axis.text.y =  element_blank(), 
        legend.position = "none",  
        rect = element_rect(fill = "transparent"),  
        plot.background = element_rect(fill = "transparent", color = NA),
        text=element_text(size=12)) #,  family="sans"
hsi_plot_post_dist_back



###to combine and save with growth analyses: 
hsi_draw_plot
hsi_plot_post_dist_back


```


###plots for total effect model - Growth-------
```{r}
##DAGS
#PLOTS:
growth_dag_me<-conditional_effects(mod_growth_by_n15_option1, effects = "Muscle_N15_c", plot = FALSE)[[1]]
mean(dem_dat_w_site_c$Muscle_N15) #9.258909

growth_dag_me_unscale<-
  growth_dag_me%>%
  mutate(Muscle_N15 = Muscle_N15_c +9.258909)

growth_draws<-
dem_dat_w_site_c %>%
  data_grid(Muscle_N15_c = seq_range(Muscle_N15_c, n = 50),
            mean_damsel_biomass_c = 0,
            mean_turf_obs_adjusted_c = 0,
            mean_structure_c = 0) %>%
  add_epred_draws(mod_growth_by_n15_option1, ndraws = 500, re_formula = NA)

growth_draws_rescale<-
  growth_draws%>%
  mutate(Muscle_N15 = Muscle_N15_c +9.258909)


growth_draw_plot<-
dem_dat_w_site_c%>%
  ggplot(aes(x = Muscle_N15, y = Growth_residuals))+
  geom_line(data = growth_draws_rescale, aes(y = .epred, x = Muscle_N15, group = .draw), color = "grey", alpha = .2, lwd = .5) +
    #ylab(expression(Surgeonfish~italic(delta)^15*N)) +
    # xlab(expression(Seabird~breeding~biomass~(kg~ha^-1))) +
     geom_line(data = growth_dag_me_unscale, aes(y = estimate__), alpha = .9, lwd = 1) +
  # geom_point(color = "#d0e2af", fill = "#d0e2af", size = 4, alpha = .8)+
     geom_point(color = "#f5db99", fill = "#f5db99", size = 3, alpha = .8)+
       xlab(expression(Surgeonfish~italic(delta)^15*N)) +
  ylab("Growth (residuals)")+
  theme_bw() +
   theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.title = element_blank(),
        legend.direction = "horizontal",
       #legend.position = "none"#,
        legend.position = "inside",
        legend.position.inside = c(.8, .8)
       )

growth_draw_plot



###posterior plot:
growth_plot_post_dist_back<-
ggplot() +
     geom_vline(xintercept=1, lty=2, alpha = .5)+
  stat_halfeye(data = as_draws_df(mod_growth_by_n15_option1), aes(x = exp(b_Muscle_N15_c),  y = 1, fill =  after_stat(x< 1)), 
               point_interval=median_hdi, .width=c(.9,.8),  slab_alpha = .9) + 
#scale_fill_manual(values = c("#0072B2", "#D55E00"	))+
   scale_fill_manual(values = c("#f5db99", "lightgrey"	))+
  theme_minimal()+
   ylab("")+
   xlab(expression(Multiplicative~effect~of~surgeonfish~italic(delta)^15*N~on~HSI)) +
   ylab("")+
 # xlim(c(-1,2))+
   xlab("")+
  theme_bw()+
   theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(), 
        axis.ticks.y =  element_blank(), 
        axis.text.y =  element_blank(), 
        legend.position = "none",  
        rect = element_rect(fill = "transparent"),  
        plot.background = element_rect(fill = "transparent", color = NA),
        text=element_text(size=12)) #,  family="sans"
growth_plot_post_dist_back



###to combine and save with growth analyses: 
growth_draw_plot
growth_plot_post_dist_back


```

###combine and save plots: 
```{r}
tot_hsi_plots_c<-
  ggdraw() +
  draw_plot(hsi_draw_plot) +
  draw_plot(hsi_plot_post_dist_back, x = 0.6, y = .6, width = .35, height = .35)
tot_hsi_plots_c

tot_growth_plots_c<-
  ggdraw() +
  draw_plot(growth_draw_plot) +
  draw_plot(growth_plot_post_dist_back, x = 0.6, y = .6, width = .35, height = .35)
tot_growth_plots_c


dem_plots<-plot_grid( tot_hsi_plots_c,  tot_growth_plots_c,   ncol = 2, labels = "auto")
dem_plots


ggsave(filename = "../outputs/figures/demographic_n15_plots.jpg", 
       plot = dem_plots,
       width = 20,
      height = 8,
       units = "cm",
       dpi = 300)
```




###re-run for all predictors with centered and scaled for plotting------
#HSI
```{r, message = FALSE}

#center AND SCALE----
dem_dat_w_site_cs<-
  dem_dat_w_site%>%
  ungroup()%>%
      mutate(log_HSI = log(HSI),
             log_wave_energy_manual = log(wave_energy_manual),
             log_pred = log(mean_predator_biomass + 1),
       Muscle_N15_cs = base::scale(Muscle_N15, center = TRUE, scale = TRUE),
          mean_atri_biomass_cs = base::scale(mean_atri_biomass, center = TRUE, scale = TRUE),
           mean_predator_biomass_cs = base::scale(mean_predator_biomass, center = TRUE, scale = TRUE),
          mean_damsel_biomass_cs = base::scale(mean_damsel_biomass, center = TRUE, scale = TRUE),
         mean_turf_obs_adjusted_cs = base::scale(mean_turf_obs_adjusted, center = TRUE, scale = TRUE),
         mean_structure_cs =  base::scale(mean_structure, center = TRUE, scale = TRUE),
         wave_cs = base::scale(wave_energy_manual, center = TRUE, scale = TRUE),
         log_wave_cs = base::scale(log_wave_energy_manual, center = TRUE, scale = TRUE),
       bites_per_minute_cs = base::scale(bites_per_minute, center = TRUE, scale = TRUE),
       distance_per_minute_cs = base::scale(distance_per_minute, center = TRUE, scale = TRUE))
  

###TOTAL effect wtih lognormal family :
cs_mod_hsi_n15 <- brm(HSI  ~ Muscle_N15_cs + mean_damsel_biomass_cs + mean_structure_cs + mean_turf_obs_adjusted_cs + (1|site),
                data=dem_dat_w_site_cs,family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/cs_mod_hsi_n15") #worked
print(cs_mod_hsi_n15)

plot(cs_mod_hsi_n15, ask = FALSE)
pp_check(cs_mod_hsi_n15) #looks good


hypothesis(cs_mod_hsi_n15, c("Muscle_N15_cs>0"))  #0.91 - still good. 

```



#Total effects of all variables on HSI:-----
```{r, message = FALSE}

#reminder of N15 effects: ------
print(cs_mod_hsi_n15)

###Atri biomass-----
cs_mod_hsi_by_atri_bio <- brm(HSI  ~ mean_atri_biomass_cs + mean_predator_biomass_cs + mean_structure_cs + mean_turf_obs_adjusted_cs + Muscle_N15_cs + (1|site),
                data=dem_dat_w_site_cs,family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/cs_mod_hsi_by_atri_bio") #worked
print(cs_mod_hsi_by_atri_bio)

###Predators-----
cs_mod_hsi_by_pred <- brm(HSI  ~  mean_predator_biomass_cs + mean_structure_cs  + (1|site),
                data=dem_dat_w_site_cs,family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/cs_mod_hsi_by_pred") #worked
print(cs_mod_hsi_by_pred)

###Structure-----
cs_mod_hsi_by_struct <- brm(HSI  ~    mean_structure_cs  + log_wave_cs + (1|site),
                data=dem_dat_w_site_cs,family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/cs_mod_hsi_by_struct") #worked
print(cs_mod_hsi_by_struct)


###turf cover-----
cs_mod_hsi_by_turf_cover<- brm(HSI  ~    mean_turf_obs_adjusted_cs  + mean_damsel_biomass_cs + Muscle_N15_cs + mean_structure_cs + (1|site),
                data=dem_dat_w_site_cs,family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/cs_mod_hsi_by_turf_cover") #worked
print(cs_mod_hsi_by_turf_cover)


###individual size-----
dem_dat_w_site_cs_size<-
  dem_dat_w_site_c%>%
  mutate(TL_cm_cs = base::scale(TL_cm, center = TRUE, scale = TRUE))

cs_mod_hsi_by_size<- brm(HSI  ~    TL_cm_cs  + (1|site),
                data=dem_dat_w_site_cs_size,family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/cs_mod_hsi_by_size") #worked
print(cs_mod_hsi_by_size)

```


###growth residuals models: CENTERED AND SCALED------
```{r}

###TOTAL effect of N15:---------
cs_mod_growth_by_n15_option1 <- brm(Growth_residuals  ~ Muscle_N15_cs + mean_damsel_biomass_cs + mean_structure_cs + mean_turf_obs_adjusted_cs + (1|site),
                data=dem_dat_w_site_cs,
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/cs_mod_growth_by_n15_option1") #worked
print(cs_mod_growth_by_n15_option1)


###Atri biomass-----
cs_mod_growth_by_atri_bio <- brm(Growth_residuals  ~ mean_atri_biomass_cs + mean_predator_biomass_cs + mean_structure_cs + mean_turf_obs_adjusted_cs + Muscle_N15_cs + (1|site),
                data=dem_dat_w_site_cs,
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/cs_mod_growth_by_atri_bio") #worked
print(cs_mod_growth_by_atri_bio)


###Predators-----
cs_mod_growth_by_pred <- brm(Growth_residuals  ~  mean_predator_biomass_cs + mean_structure_cs  + (1|site),
                data=dem_dat_w_site_cs,
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/cs_mod_growth_by_pred") #worked
print(cs_mod_growth_by_pred)



##size
cs_mod_growth_by_size<- brm(Growth_residuals  ~    TL_cm_cs  + (1|site),
                data=dem_dat_w_site_cs_size,
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/cs_mod_growth_by_size") #worked
print(cs_mod_growth_by_size)


###Structure-----
cs_mod_growth_by_struct <- brm(Growth_residuals  ~    mean_structure_cs  + log_wave_cs + (1|site),
                data=dem_dat_w_site_cs,
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/cs_mod_growth_by_struct") #worked
print(cs_mod_growth_by_struct)



###turf cover-----
cs_mod_growth_by_turf_cover<- brm(Growth_residuals  ~    mean_turf_obs_adjusted_cs  + mean_damsel_biomass_cs + Muscle_N15_cs + mean_structure_cs + (1|site),
                data=dem_dat_w_site_cs,
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/cs_mod_growth_by_turf_cover") #worked
print(cs_mod_growth_by_turf_cover)



```



####re-plot centered and scaled:-----

###plots for all dag effects -------####PLOT MODELS FOR OTHER PREDICTORS:------
```{r}

###combine all together: ------

all_causal_plot_dem_cs<-
ggplot() +
      geom_vline(xintercept=0, lty=2, alpha = .5)+
  #HSI: 
  stat_pointinterval(data = as_draws_df(cs_mod_hsi_n15 ), aes(x = (b_Muscle_N15_cs),  y = 3.1,  color = "1Dark"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
  stat_pointinterval(data = as_draws_df(cs_mod_hsi_by_turf_cover), aes(x = (b_mean_turf_obs_adjusted_cs),  y = 1.1,  color = "1Dark"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
  stat_pointinterval(data = as_draws_df(cs_mod_hsi_by_struct), aes(x = (b_mean_structure_cs),  y = 5.1,  color = "1Dark"),  
               point_interval=median_hdi, .width=c(.9,.8)) + 
      stat_pointinterval(data = as_draws_df(cs_mod_hsi_by_atri_bio), aes(x = (b_mean_atri_biomass_cs),  y = 4.1,  color = "1Dark"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
    stat_pointinterval(data = as_draws_df(cs_mod_hsi_by_pred), aes(x = (b_mean_predator_biomass_cs),  y = 6.1,  color = "1Dark"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
      stat_pointinterval(data = as_draws_df(cs_mod_hsi_by_size), aes(x = (b_TL_cm_cs),  y = 2.1,  color = "1Dark"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
  #growth:
    stat_pointinterval(data = as_draws_df(cs_mod_growth_by_n15_option1 ), aes(x = (b_Muscle_N15_cs),  y = 3,  color = "2Light"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
  stat_pointinterval(data = as_draws_df(cs_mod_growth_by_turf_cover), aes(x = (b_mean_turf_obs_adjusted_cs),  y = 1,  color = "2Light"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
  stat_pointinterval(data = as_draws_df(cs_mod_growth_by_struct), aes(x = (b_mean_structure_cs),  y = 5,  color = "2Light"), 
               point_interval=median_hdi, .width=c(.9,.8)) +  #mod_growth_by_struct
      stat_pointinterval(data = as_draws_df(cs_mod_growth_by_atri_bio), aes(x = (b_mean_atri_biomass_cs),  y = 4,  color = "2Light"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
    stat_pointinterval(data = as_draws_df(cs_mod_growth_by_pred), aes(x = (b_mean_predator_biomass_cs),  y = 6,  color = "2Light"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 
      stat_pointinterval(data = as_draws_df(cs_mod_growth_by_size), aes(x = (b_TL_cm_cs),  y = 2,  color = "2Light"), 
               point_interval=median_hdi, .width=c(.9,.8)) + 

  
  scale_y_continuous(breaks = c( 6, 5, 4, 3, 2, 1), labels = c( "Predator biomass", "Structural complexity", "Surgeonfish biomass",  expression(Surgeonfish~italic(delta)^15*N), "Surgeonfish size", "Turf cover"))+ #"Surgeonfish nutrients"
  
    scale_color_manual(values = c("1Dark" = "#c4a647", "2Light" = "#f5db99"),  name = " ", labels = c("Condition (HSI)", "Growth (residuals)"))+ 

   ylab("")+
   xlab("Effect on demographics")+
  theme_bw()+
   theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(), 
        legend.position.inside = TRUE,
        legend.position = c(.01, .01),  
        legend.justification = c("left", "bottom"),
        rect = element_rect(fill = "transparent"),  
        plot.background = element_rect(fill = "transparent", color = NA),
        text=element_text(size=17)) #,  family="sans"

all_causal_plot_dem_cs

##save plot-------
ggsave(filename = "../outputs/figures/demographics_all_causal_plots_scaled.jpg", 
       plot = all_causal_plot_dem_cs,
   width = 15,
      height = 25,
       units = "cm",
       dpi = 300)


```



###also plot growth curve for supp:
```{r}
growth_mod_acan1_newdat<-readRDS(file = "../outputs/brms/growth_mod_acan1_newdat.rds")

growth_mod_acan1_newdat


acan_growth_me<- conditional_effects(growth_mod_acan1_newdat, plot = FALSE)[[1]]
acan_growth_me

acan_growth_me_unscale<-
  acan_growth_me%>%
  mutate(TL_cm = exp(llength),
         exp_est = exp(estimate__),
         exp_lwr = exp(lower__),
         exp_upr = exp(upper__))


vbgf_draws<-
dem_dat_w_site_c %>%
   data_grid(Age = seq_range(Age, n = 50)) %>%
  add_epred_draws(growth_mod_acan1_newdat, ndraws = 500, re_formula = NA)
vbgf_draws


growth_curve_draw_plot<-
dem_dat_w_site_c%>%
  ggplot(aes(x = Age, y = TL_cm))+
  geom_line(data = vbgf_draws, aes(y = exp(.epred), x = Age, group = .draw), color = "grey", alpha = .2, lwd = .5) +
     geom_line(data = acan_growth_me_unscale, aes(y = exp_est), alpha = .9, lwd = 1) +
  # geom_point(color = "#d0e2af", fill = "#d0e2af", size = 4, alpha = .8)+
    # geom_point(color = "#f5db99", fill = "#f5db99", size = 4, alpha = .8)+
      geom_jitter(width = .2, height = 0, color = "#f5db99", fill = "#f5db99", size = 3, alpha = .8)+
     xlab(expression(Surgeonfish~italic(delta)^15*N)) +
  ylab("Total length (cm)")+
  xlab("Age (years)")+
  scale_x_continuous(breaks  = c(2, 4, 6, 8, 10, 12))+
  theme_bw() +
   theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.title = element_blank(),
        legend.direction = "horizontal",
       #legend.position = "none"#,
        legend.position = "inside",
        legend.position.inside = c(.8, .8)
       )

growth_curve_draw_plot




###save:------
# Can save the plot with ggsave()
ggsave(filename = "../outputs/figures/growth_curve_draw_plot.jpg",        plot = growth_curve_draw_plot,   width = 11, height = 11,  units = "cm",  dpi = 300)


```




##------------------seabird vs musclen15: DAG------------------ 
```{r}

acan_n15_sb_n_logwave <- brm(Muscle_N15  ~ mean_seabird_n_input_c + log_wave_c + (1|site),
                data=dem_dat_w_site_c,
                                family = lognormal(),
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/acan_n15_sb_n_logwave") #worked
print(acan_n15_sb_n_logwave)

hypothesis(acan_n15_sb_n_logwave, "mean_seabird_n_input_c>0") #0.91

pp_check(acan_n15_sb_n_logwave)


acan_n15_sb_n_logwave%>%
  spread_draws(b_mean_seabird_n_input_c)%>%
  median_hdi(exp(b_mean_seabird_n_input_c*100))#for each 100 kg/ha/yr increase, 
#1.070932	0.9569429	1.190677	
1-0.9569429
#7.09%, -4.31% to 19.07%

acan_n15_sb_n_logwave%>%
  spread_draws(b_mean_seabird_n_input_c)%>%
  median_hdi(exp(b_mean_seabird_n_input_c))
#1.000686	0.9996224	1.001797	
#6.86%, -3.78 to 17.97%
1-0.9996224

range(dem_dat_w_site_c$mean_seabird_n_input)

###PLOT------
sb_n15_plot_post_dist<-
ggplot() +
   geom_vline(xintercept=1, lty=2, alpha = .5)+
  stat_halfeye(data = as_draws_df(acan_n15_sb_n_logwave), aes(x = exp(b_mean_seabird_n_input_c*100),  y = 1, fill =  after_stat(x< 1)), 
               point_interval=median_hdi, .width=c(.9,.8),  slab_alpha = .9) + 
#scale_fill_manual(values = c("#0072B2", "#D55E00"	))+
  scale_fill_manual(values = c("#7bbcd5", "lightgrey"	))+ #e89c81
  theme_minimal()+
   ylab("")+
    xlab(expression(Effect~of~seabirds~on~fish~italic(delta)^15*N)) +
   ylab("")+
   # scale_x_continuous(limits = c(.7,2), breaks = c(.75, 1.0, 1.25, 1.5, 1.75, 2.0))+ #make match turf - nevermind looks bad
 # xlim(c(-1,2))+
 #  xlab("")+
  theme_bw()+
   theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(), 
        axis.ticks.y =  element_blank(), 
        axis.text.y =  element_blank(), 
        legend.position = "none",  
        rect = element_rect(fill = "transparent"),  
        plot.background = element_rect(fill = "transparent", color = NA),
        text=element_text(size=18)) #,  family="sans"
sb_n15_plot_post_dist

  


ggsave(filename = "../outputs/figures/sb_fishn15_plot_post_dist_exp.svg",  #.jpg
       plot = sb_n15_plot_post_dist,
       width = 11,
       height = 7.5,
       units = "cm",
       dpi = 300)



```


##testing effect of capture period to display in supp
```{r}

library(lme4)
library(car)

dem_dat_w_site_capt<-
  dem_dat_w_site%>%
  mutate(Capture_period = case_when(Capture_year == 2021 & Capture_month <=8 ~"June_2021",
                                    Capture_year == 2021 & Capture_month >9 ~"Nov_2021",
                                    Capture_year == 2022 ~"June_2022"))

gsi_lm<-lmer(GSI~Capture_period + (1|site), data = dem_dat_w_site_capt)
summary(gsi_lm)
Anova(gsi_lm)
#                Chisq Df Pr(>Chisq)  
#Capture_period 6.8039  2    0.03331 *


hsi_lm<-lmer(HSI~Capture_period + (1|site), data = dem_dat_w_site_capt)
summary(hsi_lm)
Anova(hsi_lm)
#                Chisq Df Pr(>Chisq)
#Capture_period 0.5101  2     0.7749

n15_lm<-lmer(Muscle_N15~Capture_period + (1|site), data = dem_dat_w_site_capt)
summary(n15_lm)
Anova(n15_lm)
#               Chisq Df Pr(>Chisq)
#Capture_period 0.7527  2     0.6864

```

